# Parallel set of non-Bayesian analyses

In this appendix, we report the output of a parallel set of non-Bayesian linear mixed-effects models for the primary analyses (Reaction Time, Accuracy, EWMA) in Experiments 1 and 2. The $p$ values for each coefficient were computed via the Satterthwaite approximation using the `lmerTest` R package (Kuznetsova, Brockhoff, & Christensen, 2017). 

```{r helpers}
clean_p_vals <- function(x) {
  case_when(x < .001 ~ "< .001",
            x < .01 ~ "< .01", 
            TRUE ~ round(x, 2) %>% as.character(x))
}

munge_table <- function(d, mod_type = 'multilevel', exp) {
  if (mod_type == 'multilevel') {
    d <- d %>% filter(effect == "fixed")   
  }
  
  d <- d %>% select(term:p.value) 
  
  if (exp == "e1") {
    d %>% 
      mutate(p.value = clean_p_vals(p.value),
             term = str_remove(term, "stimuli"),
             term = str_remove(term, "condition"),
             term = ifelse(term == "(Intercept)", "Intercept (ASL)", term)) %>% 
      mutate_if(is.numeric, printnum)  
  } else {
    d %>% 
      mutate(p.value = clean_p_vals(p.value),
             term = str_remove(term, "noise_condition"),
             term = str_remove(term, "age_category"),
             term = ifelse(term == "(Intercept)", "Intercept (Clear)", term)) %>% 
      mutate_if(is.numeric, printnum)  
  }
}
```

```{r mle rt trio, results = 'asis'}
trio_rt_mle <- df_trio %>% 
  mutate(log_rt = log(RT)) %>% 
  filter(age_code == "child", correct == 1, RT <= upper_bound_RT) %>% 
  lmer(log_rt ~ stimuli + scale(Months) + (1 | Sub.Num) + (1 | clean_target_img),
       data = .)

broom.mixed::tidy(trio_rt_mle) %>% 
  munge_table(mod_type =  'multilevel', exp = "e1") %>% 
  apa_table(placement = 'h', 
            note = "Model specification: log(RT) ~ stimuli + scale(Months) + (1 | subid) + (1 | target_image)",
            caption = "Output of the MLE model predicting log reaction time as a function of center stimulus type in Experiment 1.")
```

```{r mle acc trio, results = 'asis'}
trio_acc_mle <- df_trio %>% 
  filter(age_code == "child", trial_type %in% c("C_T", "C_D")) %>% 
  glmer(correct ~ stimuli + (1 | Sub.Num) + (1 | clean_target_img), 
        family = binomial(link = "logit"), 
        data = .)

broom.mixed::tidy(trio_acc_mle) %>% 
  munge_table(mod_type =  'multilevel', exp = "e1") %>% 
  apa_table(placement = 'h',
            note = "Model specification: correct ~ stimuli + (1 | subid) + (1 | target_image)",
            caption = "Output of the MLE model predicting accuracy as a function of center stimulus type in Experiment 1.")
```

```{r mle ewma trio prop lang, results = 'asis'}
trio_ewma_mle <- d_ewma_trio %>% 
  filter(age_code == "child", stimuli %in% c("ASL", "Face")) %>% 
  glmer(guess_num ~ stimuli + (1|subid) + (1|clean_target_img),
        family = binomial(link = "logit"),
        data = .)

broom.mixed::tidy(trio_ewma_mle) %>% 
  munge_table(mod_type =  'multilevel', exp = "e1") %>% 
  apa_table(placement = 'h',
            note = "Model specification: guess ~ stimuli + (1 | subid) + (1 | target_image)",
            caption = "Output of the MLE model estimating the difference in random responding in the EWMA as a function of center stimulus type in Experiment 1.")
```

```{r mle rt noise, results = 'asis'}
noise_rt_mle <- d_noise_analysis %>% 
  lmer(log_rt ~ noise_condition + age_category + (noise_condition | subid) + (1 | target_image),
       data = .)

broom.mixed::tidy(noise_rt_mle) %>% 
  munge_table(mod_type =  'multilevel', exp = "e2") %>% 
  apa_table(placement = 'h',
            note = "Model specification: log(rt) ~ noise_condition + age_category + (noise_condition | subid) + (1 | target_image)",
            caption = "Output of the MLE model predicting log reaction time as a function of noise condition and age category (adults vs. children) in Experiment 2.")
```

```{r mle acc noise, results = 'asis'}
noise_acc_mle <- d_noise_analysis %>% 
  glmer(shift_acc_num ~ noise_condition + age_category + (noise_condition | subid) + (1|target_image), 
        family = binomial(link = "logit"),
        nAGQ = 0,
        data = .)

broom.mixed::tidy(noise_acc_mle) %>% 
  munge_table(mod_type =  'multilevel', exp = "e2") %>% 
  apa_table(placement = 'h',
            note = "Model specification: correct ~ noise_condition + age_category + (noise_condition | subid) + (1 | target_image)",
            caption = "Output of the MLE model predicting accuracy as a function of noise condition and age category (adults vs. children) in Experiment 2.")
```

```{r mle ewma noise, results = 'asis'}
noise_ewma_mle <- d_ewma_noise %>% 
  glmer(guess_num ~ noise_condition + age_category + (noise_condition | subid) + (noise_condition | target_image),
        family = binomial(link = "logit"),
        data = .)

broom.mixed::tidy(noise_ewma_mle) %>% 
  munge_table(mod_type =  'multilevel', exp = "e2") %>% 
  apa_table(placement = 'h',
            note = "Model specification: guess_num ~ noise_condition + age_category + (noise_condition | subid) + (noise_condition | target_image)",
            caption = "Output of the MLE model estimating the difference in random responding (EWMA model) as a function of noise condition and age category (adults vs. children) in Experiment 2.")
```

# Bayesian data analysis models: Experiment 1

In this appendix, we report the full output of the Bayesian linear mixed effects models in Experiment 1.

```{r trio-rt-model, results = 'asis'}
ms_rt_trio %>% 
  mutate(`95% HDI` = str_c("[", hdi_lower, ", ", hdi_upper, "]"),
         condition = ifelse(condition == "asl", "ASL", str_to_title(condition))) %>% 
  select(-hdi_lower, -hdi_upper) %>% 
  arrange(m_rt) %>% 
  rename(`Center Stimulus Type` = condition,
         `Mean RT` = m_rt) %>% 
  apa_table(placement = 'h',
            caption = "Output of the regression predicting reaction time (milliseconds) as a function of center stimulus type in Experiment 1.")
```

```{r trio-acc-model, results = 'asis'}
ms_acc_trio %>% 
  mutate(`95% HDI` = str_c("[", hdi_lower, ", ", hdi_upper, "]"),
         condition = ifelse(condition == "asl", "ASL", str_to_title(condition))) %>% 
  arrange(prop) %>% 
  select(-hdi_lower, -hdi_upper) %>% 
  rename(`Center Stimulus Type` = condition,
         `Mean Accuracy` = prop) %>% 
  apa_table(placement = 'h',
            caption = "Output of the logistic regression predicting accuracy as a function of center stimulus type in Experiment 1.")
```

```{r trio-acc-contrasts, results = 'asis'}
ms_contrasts_trio_acc %>% 
  mutate(`95% HDI` = str_c("[", hdi_lower, ", ", hdi_upper, "]"),
         contrast = case_when(
           contrast == "asl_face" ~ "ASL vs. Face",
           contrast == "asl_noasl" ~ "ASL vs. English",
           contrast == "face_object_bullseye" ~ "Face vs. Object/Bullseye",
           contrast == "bullseye_chance" ~ "Bullseye vs. Chance",
           contrast == "object_chance" ~ "Object vs. Chance"
         )) %>% 
  select(-hdi_lower, -hdi_upper) %>% 
  arrange(prop) %>% 
  rename(`Contrast` = contrast,
         `Mean Difference Accuracy` = prop) %>% 
  apa_table(placement = 'h',
            caption = "Output of the model estimating differences in Accuracy for specific contrasts of interest in Experiment 1.")
```

```{r trio-rt-contrasts, results = 'asis'}
ms_contrasts_trio_rt %>% 
  mutate(`95% HDI` = str_c("[", hdi_lower, ", ", hdi_upper, "]"),
         contrast = case_when(
           contrast == "asl_face" ~ "ASL vs. Face",
           contrast == "asl_noasl" ~ "ASL vs. English",
           contrast == "face_object_bullseye" ~ "Face vs. Object/Bullseye"
         )) %>% 
  select(-hdi_lower, -hdi_upper) %>% 
  arrange(rt) %>% 
  rename(`Contrast` = contrast,
         `Mean Difference RT` = rt) %>% 
  apa_table(placement = 'h',
            caption = "Output of the model estimating differences in RT for specific contrasts of interest in Experiment 1.")
```

```{r trio-ewma-cuts, results = 'asis'}
ms_cuts_trio %>% 
  mutate(`95% HDI` = str_c("[", hdi_lower, ", ", hdi_upper, "]"),
         condition = ifelse(condition == "asl", "ASL", str_to_title(condition))) %>% 
  select(-hdi_lower, -hdi_upper) %>% 
  arrange(MAP) %>% 
  rename(`Center Stimulus Type` = condition,
         `Mean EWMA Cut Point` = MAP) %>% 
  apa_table(placement = 'h',
            caption = "Output of the model estimating the point in the Reaction Time distribution when children's Exponentially Weighted Moving Average statistic crossed the pre-defined guessing threshold for the ASL and Face center stimulus types in Experiment 1.")
```

```{r trio-guess-cuts, results = 'asis'}
ms_guess_trio %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(`95% HDI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
         condition = ifelse(condition == "asl", "ASL", str_to_title(condition))) %>% 
  select(-ci_lower, -ci_upper) %>% 
  arrange(MAP) %>% 
  rename(`Center Stimulus Type` = condition,
         `Mean Language-driven` = MAP) %>% 
  apa_table(placement = 'h',
            caption = "Output of the model estimating the mean proportion of shifts categorized as language-driven by the Exponentially Weighted Moving Average model for the ASL and Face center stimulus types in Experiment 1.")
```

```{r trio-hddm, results = 'asis'}
ms.hddm_trio %>% 
  ungroup() %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(`95% HDI` = str_c("[", HDI_lower, ", ", HDI_upper, "]")) %>% 
  select(-HDI_lower, -HDI_upper) %>% 
  arrange(Parameter, Mean) %>% 
  mutate(Parameter = str_to_title(Parameter)) %>% 
  rename(`Mean Param Estimate` = Mean,
         `Center Stim Type` = condition) %>% 
  apa_table(placement = 'h',
            caption = "Summary of the Drift Diffusion Model output for the drift rate and boundary separation parameters for both all four center stimulus types in Experiment 1.")
```

# Bayesian data analysis models: Experiment 2

In this appendix, we report the full output of the Bayesian linear mixed effects models in Experiment 2.

```{r noise-acc-model, results = 'asis'}
ms_acc_noise %>% 
  ungroup() %>% 
  mutate_if(is.character, str_to_title) %>% 
  mutate(`95% HDI` = str_c("[", hdi_lower, ", ", hdi_upper, "]")) %>% 
  arrange(prop) %>% 
  select(-hdi_lower, -hdi_upper) %>% 
  rename(`Noise Condition` = noise_condition,
         `Mean Accuracy` = prop,
         `Age Group` = age_category) %>% 
  apa_table(placement = 'h',
            caption = "Output of the logistic regression predicting accuracy as a function of noise condition and age group in Experiment 2.")
```

```{r noise-rt-model, results = 'asis'}
ms_rt_noise %>% 
  ungroup() %>% 
  mutate_if(is.character, str_to_title) %>% 
  mutate(`95% HDI` = str_c("[", hdi_lower, ", ", hdi_upper, "]")) %>% 
  select(-hdi_lower, -hdi_upper) %>% 
  arrange(m_rt) %>% 
  rename(`Noise Condition` = noise_condition,
         `Mean RT` = m_rt,
         `Age Group` = age_category) %>% 
  apa_table(placement = 'h',
            caption = "Output of the regression estimating reaction times (milliseconds) as a function of noise condition and age group in Experiment 2.")
```

```{r noise-guess-cuts, results = 'asis'}
ms_guess_noise %>% 
  select(-model, -parameter) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate_if(is.character, str_to_title) %>% 
  select(noise_condition, everything()) %>% 
  mutate(`95% HDI` = str_c("[", hdi_lower, ", ", hdi_upper, "]")) %>% 
  select(-hdi_lower, -hdi_upper) %>% 
  arrange(MAP) %>% 
  rename(`Noise Condition` = noise_condition,
         `Mean Language-driven` = MAP,
         `Age Group` = age_category) %>% 
  apa_table(placement = 'h',
            caption = "Output of the model estimating the mean proportion of shifts categorized as language-driven by the Exponentially Weighted Moving Average model for the each noise condition and age group in Experiment 2.")
```

```{r noise-hddm, results = 'asis'}
hddm_table_age %>% 
  ungroup() %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(`95% HDI` = str_c("[", HDI_lower, ", ", HDI_upper, "]")) %>% 
  select(-HDI_lower, -HDI_upper) %>% 
  arrange(param_name, MAP) %>% 
  mutate(param_name = str_to_title(param_name),
         age_code = str_to_title(age_code)) %>% 
  rename(`Parameter` = param_name,
         `Mean Parameter Estimate` = MAP,
         `Age Group` = age_code) %>% 
  apa_table(placement = 'h',
            caption = "Summary of the Drift Diffusion Model output for the drift rate and boundary separation parameters for both processing contexts and age groups in Experiment 2.")
```