---
title: "Speed-Acc JEP: General Figure Visualization Code (Trio)"
output: html_document
---

## Set up 

This document contains the codebase for generating the plots for Study 1 in the paper, "An information-seeking account of children's eye movements during grounded signed and spoken language comprehension"

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb",
                      fig.path='figs/',echo=F, warning=F, cache=T, message=F, include =F,
                      sanitize = T)
```

```{r load libraries}
library(here); library(kableExtra); library(rogme); library(ggridges); library(ggrepel)
source(here::here("R/helper_functions/libraries_and_functions.R"))
source(here::here("R/helper_functions/ewma_helper_funs.R"))
```

```{r set data paths}
data_path <- "data/3_final_merged_data/first_shifts/"
time_path <- "data/3_final_merged_data/timecourse/"
models_path <- "data/3_final_merged_data/bda_posterior_samples/"
ewma_path <- "data/3_final_merged_data/ewma_output/"
hddm_path <- "data/3_final_merged_data/hddm_output/"
```

```{r read trio timecourse data}
d_time_trio <- read_csv(here::here(time_path, "speed-acc-child-timecourse.csv"))

d_time_trio %<>% mutate(stimuli = ifelse(stimuli %in% c("V1", "V2"), "ASL", 
                               ifelse(stimuli == "Trio", "Object", 
                                      ifelse(stimuli == "Bull", "Bullseye",stimuli))),
              stimuli = factor(stimuli, levels = c("ASL", "Face", "Object", "Bullseye")))

colnames(d_time_trio) <- gsub(pattern = "X", replacement = "", x = colnames(d_time_trio))
```

```{r read trio first shift data}
upper_bound_RT <- 2000

d_kids_trio <- read_csv(here::here(data_path, "speed_acc_child_trio_fstshift_tidy.csv")) 

d_kids_trio %<>% 
  mutate(stimuli = ifelse(stimuli == "V1" | stimuli == "V2", "ASL", 
                          ifelse(stimuli == "Trio", "Object", 
                                 ifelse(stimuli == "Bull", "Bullseye",
                                        stimuli))),
         stimuli = factor(stimuli, levels = c("ASL", "Face", "Object", "Bullseye"))) %>% 
  filter(RT <= upper_bound_RT, trial_type != "no_shift", age_code == "child")
```

```{r read ewma model data files}
# read in ewma files for all experiments using purrr
files <- dir(path = ewma_path, pattern = "*.csv") 
d_ewma <- files %>% purrr::map_df(read_ewma, path = ewma_path)

# hddm output for all experiments
d_hddm <- read_csv(here::here(hddm_path, "hddm_tidy.csv"))
```

```{r read bda model output}
# trio experiment
d_bda_trio <- readRDS(here::here(models_path, "speed-acc-trio-posterior-samples.rds"))
```

## Spoken vs. Sign Language 

### Trio Timecourse plot

Grab just the eye movement data and group information

```{r}
ss_iChart <- d_time_trio %>% 
  select(Sub.Num, language_modality, trial_type, stimuli, age_code, Response, `0`:`3000`) %>% 
  filter(Response == "D", age_code == "child") 
```

Convert to wide data to long format

```{r}
ss_iChart_long <- ss_iChart %>% 
  gather(key = Time.ms, value = value, `0`:`3000`) %>% 
  filter(value %in% c("0", "0.5", "1")) %>% 
  mutate(value_cat = factor(value, labels = c("Distractor", "Center", "Target")),
         Time.ms_numeric = as.numeric(Time.ms)) 
```    

Summarize proportion looking for each participant at each time slice.

```{r}
ms_iChart_count <- ss_iChart_long %>% 
  group_by(Sub.Num, Time.ms, language_modality, value_cat) %>% 
  dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
  dplyr::summarise(sum_count = sum(count)) %>% 
  ungroup() %>% 
  mutate(Sub.Num = as.character(Sub.Num))

ms_iChart <- as.data.frame(xtabs(~ Sub.Num + value_cat + Time.ms, data = ss_iChart_long),
                           stringsAsFactors = F) %>% 
  left_join(y = ms_iChart_count, by = c("Sub.Num", "Time.ms")) %>% 
  mutate(proportion_looking = Freq / sum_count,
         language_modality_factor = as.factor(language_modality))
```

Get means and CIs for proportion looking at each time slice across particpants

```{r}
ms_iChart_count <- ss_iChart_long %>% 
  group_by(Sub.Num, Time.ms, stimuli, value_cat) %>% 
  dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
  dplyr::summarise(sum_count = sum(count)) %>% 
  ungroup() %>% 
  mutate(Sub.Num = as.character(Sub.Num))

ms_iChart <- as.data.frame(xtabs(~ Sub.Num + value_cat + Time.ms, data = ss_iChart_long),
                           stringsAsFactors = F) %>% 
  left_join(y = ms_iChart_count, by = c("Sub.Num", "Time.ms")) %>% 
  mutate(proportion_looking = Freq / sum_count,
         stimuli_factor = as.factor(stimuli))

# get means and bootsrapped CIs for each timepoint
nboot <- 500

ms_mean_iChart <- ms_iChart %>% 
  group_by(Time.ms, stimuli, value_cat) %>% 
  langcog::multi_boot_standard(column = "proportion_looking", na.rm = T, nboot = nboot) %>% 
  filter(is.na(stimuli) == F) %>% 
  ungroup() %>% 
  mutate(Time.ms = as.numeric(Time.ms))

write_csv(x = ms_mean_iChart, 
          path = here::here("paper/journal_submission/figures/trio_timecourse_graph_vals.csv"))
```

Now we make Tanenhaus style plot.

```{r make tanenhaus-plot trio}
# change factor levels for plot to help compare conditions of interest
ms_mean_iChart$stimuli <- factor(ms_mean_iChart$stimuli, 
                                 levels = c("ASL", "Face", "Object", "Bullseye"))

trio_timecourse <- ms_mean_iChart %>% 
  filter(Time.ms <= 2500) %>% 
  ggplot(aes(x = as.numeric(Time.ms), y = mean, color = value_cat), 
       data = .) + 
  ylim(-.1,1) +
  xlim(0,3000) +
  geom_line(size=0.7) +
  geom_linerange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), alpha = 0.5) +
  scale_color_manual(values = c("grey70", "grey50", "grey1")) +
  xlab("Time from noun onset (ms)") +
  ylab("Proportion looking") +
  guides(color = F) +
  geom_rect(aes(xmin = 0, xmax = 2000, ymin = -Inf, ymax = -.1), alpha = 0.1, 
            fill = "grey70", color = NA) +
  facet_wrap(~stimuli, ncol = 1) +
  theme(plot.margin = unit(c(1,4,1,1), "lines")) + 
  geom_text_repel(
    data = filter(ms_mean_iChart, Time.ms == 2500),
    aes(label = value_cat),
    size = 4,
    nudge_x = 55,
    segment.color = NA
  ) 
```

### Trio First shift accuracy plot

```{r get mean acc for each participant trio}
ss_trio <- d_kids_trio %>% 
  group_by(Sub.Num, age_code, Months, language_modality, 
           stimuli, hearing_status_participant) %>% 
  filter(trial_type != "no_shift") %>% 
  summarise(mean_correct = mean(correct),
            m_rt = median(RT_sec))
```


```{r set global plot values}
pt_size <- 2.5
pt_alpha <- 0.6
pt_shape <- 21
pt_width <- 0.2
pt_color <- "black"
pt_fill <- "darkgrey"
```

```{r make trio acc plot}
p_acc_trio <- ss_trio %>% 
  ggplot(aes(x = fct_rev(stimuli), y = mean_correct)) +
  ggbeeswarm::geom_quasirandom(shape = pt_shape, 
                               width = pt_width, 
                               color = pt_color, 
                               size = pt_size,
                               fill = pt_fill,
                               alpha = pt_alpha) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  labs(x = NULL, y = "Prop. Correct") +
  lims(y = c(0, 1)) 

# get model values
d_model_vals <- d_bda_trio$acc_trio_contin %>%
  select(sample_id, contains("prob")) %>% 
  select(-age_beta_prob) %>% 
  dplyr::rename(ASL = asl_prob,
                Bullseye = bullseye_prob,
                Face = face_prob,
                Object = object_prob) %>% 
  gather(key = stimuli, value = mean_correct, -sample_id)

d_quantiles <- d_model_vals %>% 
  group_by(stimuli) %>% 
  summarise(ci_lower = hd(mean_correct, q = 0.025),
            ci_upper = hd(mean_correct, q = 0.975),
            mean_correct = hd(mean_correct, q = 0.5))

# add quantiles to plot
p_acc_trio <- p_acc_trio +
  geom_pointrange(aes(ymax = ci_upper, ymin = ci_lower), 
                  data = d_quantiles,
                  color = "red",
                  shape = 15,
                  size = 0.7)

p_acc_trio
```

### Trio First shift RT plot 

```{r make trio rt plot}
p_rt_trio <- ss_trio %>% 
  filter(age_code == "child") %>% 
  ggplot(aes(x = fct_rev(stimuli), y = m_rt)) +
  ggbeeswarm::geom_quasirandom(shape = pt_shape, 
                               width = pt_width, 
                               color = pt_color, 
                               size = pt_size,
                               fill = pt_fill,
                               alpha = pt_alpha) +  
  ylim(0, 1.8) +
  labs(y = "RT (sec)", x = NULL) +
  coord_flip()

# get model values
d_model_vals <- d_bda_trio$rt_trio_contin %>%
  select(sample_id, contains("scale")) %>% 
  select(-age_beta_rt_scale) %>% 
  dplyr::rename(ASL = asl_rt_scale,
                Bullseye = bullseye_rt_scale,
                Face = face_rt_scale,
                Object = object_rt_scale) %>% 
  gather(key = stimuli, value = rt_msec, -sample_id) %>% 
  mutate(RT_sec = rt_msec / 1000)

# add model values to plot
d_quantiles <- d_model_vals %>% 
  group_by(stimuli) %>% 
  summarise(ci_lower = hd(RT_sec, q = 0.025),
            ci_upper = hd(RT_sec, q = 0.975),
            m_rt = hd(RT_sec, q = 0.5))

p_rt_trio <- p_rt_trio +
  geom_pointrange(aes(ymax = ci_upper, ymin = ci_lower), 
                  data = d_quantiles,
                  color = "red",
                  shape = 15,
                  size = 0.7)

p_rt_trio
```

### Merge behavioral plots and save

```{r}
trio_fst_shifts <- plot_grid(p_rt_trio, p_acc_trio, ncol = 1)
trio_behav_plot <- plot_grid(trio_timecourse, trio_fst_shifts, rel_widths = c(1, 0.7))

save_plot(filename = here::here("paper/journal_submission/figures/figs_output/fig1_trio_behav.png"), 
          trio_behav_plot,
          ncol = 3,
          nrow = 2,
          base_aspect_ratio = 1)
```

### Model visualizations

Make trio control chart

```{r make trio control plot}
# make control plot
trio_ewma_vals <- d_ewma %>% 
  filter(rt <= 1.5, experiment == "trio", age_code == "child") %>% 
  aggregate_ewma

trio_ewma_vals$ewma_summary$condition <- factor(trio_ewma_vals$ewma_summary$condition, 
                                                levels = c("ASL", "Face", "Object", "Bullseye"))

trio_ewma_vals$cutoff_summary$condition <- factor(trio_ewma_vals$cutoff_summary$condition, 
                                                levels = c("ASL", "Face", "Object", "Bullseye"))

trio_control_plot <- trio_ewma_vals %>% plot_ewma_chart()
trio_control_plot <- trio_control_plot + theme(plot.margin = unit(c(1,4,1,1), "lines"))
```

```{r make trio boxplots of guessing}
p_ewma_trio <- d_ewma %>% 
  filter(rt <= 1.5, experiment == "trio", age_code == "child") %>% 
  group_by(subid, condition, guess) %>% 
  summarise(count = n()) %>% 
  mutate(prop.responding = round(count / sum(count), 2)) %>% 
  filter(guess == "response") %>% 
  ggplot(aes(x = fct_reorder(condition, prop.responding), y = prop.responding)) +
  ggbeeswarm::geom_quasirandom(shape = pt_shape, 
                               width = pt_width, 
                               color = pt_color, 
                               size = pt_size,
                               fill = pt_fill,
                               alpha = pt_alpha) +
  lims(y = c(0,1)) +
  labs(x = "Condition", y = "Prop. Language-driven")  +
  scale_x_discrete(expand = c(0,1)) 

d_quantiles_ewma <- d_bda_trio$ewma_guess_trio %>% 
  mutate(asl_kids = asl - age_beta,
         face_kids = face - age_beta) %>% 
  select(asl_kids, face_kids) %>% 
  rename(ASL = asl_kids, Face = face_kids) %>% 
  gather(key = condition, value = param_estimate) %>% 
  mutate(param_est_prob = logit_to_prob(param_estimate)) %>% 
  group_by(condition) %>% 
  summarise(ci_lower = hd(param_est_prob, q = 0.025),
            ci_upper = hd(param_est_prob, q = 0.975),
            prop.responding = hd(param_est_prob, q = 0.5))

# add quantiles to plot
p_ewma_trio <- p_ewma_trio +
  geom_pointrange(aes(ymax = ci_upper, ymin = ci_lower), 
                  data = d_quantiles_ewma,
                  color = "red",
                  shape = 15,
                  size = 0.7)
```

Make hddm plots

```{r make trio hddm plot}
x_lims <- c(0, 2)

p_hddm_trio <- d_hddm %>% 
  filter(experiment == "trio", age_code == "children") %>% 
  ggplot(aes(x = param_value, y = param_name, fill = condition)) +
  geom_density_ridges(scale = 0.7, rel_min_height = 0.005, alpha = 0.8) + 
  labs(x = "Parameter value", y = NULL, color = "") +
  lims(x = x_lims)  +
  scale_y_discrete(expand = c(0.2,0)) +
  theme(legend.position=c(0.85,0.8)) +
  scale_fill_grey()
```

Put trio model plots together.

```{r put model plots together}
trio_ewma_hddm_plots <- plot_grid(p_ewma_trio, p_hddm_trio, ncol = 1, labels = c("B", "C"))
trio_final_model_plot <- plot_grid(trio_control_plot, trio_ewma_hddm_plots, ncol = 2,
                                   rel_widths = c(1, 0.8),
                                   labels = "A")

save_plot(filename = here::here("paper/journal_submission/figures/figs_output/fig2_trio_models.png"), 
          trio_final_model_plot,
          ncol = 3,
          nrow = 2,
          base_aspect_ratio = 1)
```

