---
title: "Speed-Acc JEP: General Figure Visualization Code (Text)"
output: html_document
---

## Set up 

This document contains the codebase for generating the plots for Study 2 in the paper, "An information-seeking account of children's eye movements during grounded signed and spoken language comprehension"

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb",
                      fig.path='figs/',echo=F, warning=F, cache=T, message=F, include =F,
                      sanitize = T)
```

```{r load libraries}
source(here::here("R/helper_functions/libraries_and_functions.R"))
source(here::here("R/helper_functions/ewma_helper_funs.R"))
source(here::here("R/helper_functions/paper_helpers.R"))

# data paths
data_path <- "data/3_final_merged_data/first_shifts/"
time_path <- "data/3_final_merged_data/timecourse/"
models_path <- "data/3_final_merged_data/bda_posterior_samples/"
ewma_path <- "data/3_final_merged_data/ewma_output/"
hddm_path <- "data/3_final_merged_data/hddm_output/"
```

```{r read data}
# timecourse
d_timecourse <- read_csv(here::here(time_path, "speed_acc_adult_text_timecourse_tidy.csv.gz"))
d_timecourse %<>% filter(t.stim > 0, t.stim <= 5) 

#  first shift data
d_fst <- read_csv(here::here(data_path, "speed_acc_adult_text_fstshift_tidy.csv"))

# ewma files for all experiments using purrr
files <- dir(path = ewma_path, pattern = "*.csv") 
d_ewma <- files %>% purrr::map_df(read_ewma, path = ewma_path)

# hddm output for all experiments
d_hddm <- read_csv(here::here(hddm_path, "hddm_tidy.csv"))

# read bda model output}
d_bda <- readRDS(here::here(models_path, "speed-acc-text-posterior-samples.rds"))
```

## Text Processing Plots

### Timecourse plots

```{r}
d_time_filt <- d_timecourse %>% 
  filter(t.rel.noun >= 0, t.rel.noun <= 2)

# get number of trials looking at each gaze target for each time slice
ss.d <- d_time_filt %>% 
  group_by(subid, t.stim, condition) %>% 
  summarise(count = n()) %>% 
  ungroup() %>% 
  complete(nesting(subid, t.stim), condition,
           fill = list(count = 0)) %>% 
  mutate(subid = as.character(subid))

# get proportion looking by dividing the freq looking at each target by the total looking 
# derived in step 1 of this chunk
ss.d <- as.data.frame(xtabs(~ subid + t.stim + target_looking + condition, 
                            data = d_time_filt),
                      stringsAsFactors = F) %>% 
  mutate(t.stim = as.numeric(t.stim)) %>% 
  left_join(x = ss.d, y = ., by = c("subid", "t.stim", "condition")) %>% 
  mutate(proportion_looking = Freq / count)
```

Get means and CIs for proportion looking at each time slice across participants. Note that this stores the graph values in a file for reading in later in the analysis. 

```{r, eval = F}
# get means and bootsrapped CIs for each timepoint, nboot should be 500
nboot <- 500

ms_mean_iChart <- ss.d %>% 
  group_by(t.stim, condition, target_looking) %>% 
  langcog::multi_boot_standard(col = "proportion_looking", na.rm = T, nboot = nboot) %>% 
  filter(is.na(condition) == F) %>% 
  ungroup() %>% 
  mutate(t.stim = as.numeric(t.stim - 3.3)) # make t.stim relative to noun onset

write_csv(x = ms_mean_iChart, 
          path = here::here("paper/journal_submission/figures/text_timecourse_graph_vals.csv"))
```

Make plot.

```{r}
text_time_gvs <- read_csv(here::here("paper/journal_submission/figures/text_timecourse_graph_vals.csv"))

text_timecourse_plot <- ggplot(aes(x = as.numeric(t.stim), y = mean, 
           color = target_looking), 
           data = text_time_gvs) + 
  geom_line(size=0.7) +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.5) +
  scale_color_brewer(palette="Dark2") +
  xlab("Time from noun onset (sec)") +
  ylab("Proportion looking") +
  guides(color = F, linetype = F) +
  facet_wrap(~condition, ncol = 1) +
  geom_text_repel(
    data = filter(text_time_gvs, t.stim == max(t.stim)),
    aes(label = target_looking),
    size = 4,
    nudge_x = 0.1,
    segment.color = NA
  ) +
  ylim(-0.01,1.01) +
  xlim(0,2) 

text_timecourse_plot
```

### First shifts plots

Filter data

```{r}
d_fst %<>% 
  filter(shift_type %in% c("C_T", "C_D"), 
         response_onset_type %in% c("noun")) %>% 
  dplyr::select(subid, tr.num, condition, shift_accuracy, rt, response_onset_type) %>%
  mutate(correct_num = ifelse(shift_accuracy == "correct", 1, 0)) %>% 
  unique()
```

Aggregate for accuracy and RT

```{r}
ss <- d_fst %>% 
  group_by(condition, subid) %>% 
  summarise(m_acc = mean(correct_num),
            m_rt = mean(rt))
```

Make first shift accuracy plot.

```{r set global plot values}
pt_size <- 3.5
pt_alpha <- 0.5
pt_shape <- 21
pt_width <- 0.15
pt_color <- "black"
pt_fill <- "darkgrey"
nboot <- 500
```

First shift accuracy plot.

```{r make text acc plot}
p_acc <- ss %>% 
  ggplot(aes(x = fct_relevel(condition, "face", after = 3), y = m_acc)) +
   ggbeeswarm::geom_quasirandom(shape = pt_shape, 
                               width = pt_width, 
                               color = pt_color, 
                               size = pt_size,
                               fill = "grey",
                               alpha = pt_alpha) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  guides(fill=F) +
  labs(x = NULL, y = "Prop. Correct") +
  lims(y = c(0, 1)) 

# get model values
d_model_vals <- d_bda$acc_text %>%
  mutate(`text-no-audio` = text_no_audio + bullseye_int,
         face = bullseye_int + face,
         text = bullseye_int + text) %>% 
  rename(bullseye = bullseye_int) %>% 
  select(-text_no_audio) %>% 
  gather(key = condition, value = mean_correct, -sample_id) %>% 
  mutate(mean_correct = logit_to_prob(mean_correct))

d_quantiles <- d_model_vals %>% 
  group_by(condition) %>% 
  summarise(ci_lower = hd(mean_correct, q = 0.025),
            ci_upper = hd(mean_correct, q = 0.975),
            m_acc = hd(mean_correct, q = 0.5))

# add quantiles to plot
p_acc <- p_acc +
  geom_pointrange(aes(ymax = ci_upper, ymin = ci_lower), 
                  data = d_quantiles,
                  color = "grey20",
                  shape = 15,
                  size = 0.7)

p_acc
```

First shift RT plot.

```{r make text rt plot}
p_rt <- ss %>% 
  ungroup() %>% 
  mutate(condition = fct_relevel(condition, c("bullseye", "text", "face", "text-no-audio"))) %>% 
  ggplot(aes(x = fct_rev(condition), 
             y = m_rt,
             fill = condition)) +
   ggbeeswarm::geom_quasirandom(shape = pt_shape, 
                               width = pt_width, 
                               color = pt_color, 
                               size = pt_size,
                               fill = "grey",
                               alpha = pt_alpha) + 
  ylim(0, 1.3) +
  guides(fill = F) + 
  labs(y = "RT (sec)", x = NULL) +
  coord_flip()

# get model values
d_model_vals <- d_bda$rt_text %>%
  mutate(`text-no-audio` = text_no_audio + bullseye_int,
         face = bullseye_int + face,
         text = bullseye_int + text) %>% 
  rename(bullseye = bullseye_int) %>% 
  select(-text_no_audio) %>% 
  gather(key = condition, value = mean_rt, -sample_id) %>% 
  mutate(m_rt = exp(mean_rt))

# add model values to plot
d_quantiles <- d_model_vals %>% 
  group_by(condition) %>% 
  summarise(ci_lower = hd(m_rt, q = 0.025),
            ci_upper = hd(m_rt, q = 0.975),
            m_rt = hd(m_rt, q = 0.5))

p_rt <- p_rt +
  geom_pointrange(aes(ymax = ci_upper, ymin = ci_lower), 
                  data = d_quantiles,
                  color = "grey20",
                  shape = 15,
                  size = 0.7)

p_rt
```

### Merge behavioral plots and save

```{r}
text_fst_shifts <- plot_grid(p_rt, p_acc, 
                             ncol = 1,
                             rel_heights = c(0.95,1), 
                             labels = c("B", "C"),
                             scale = c(0.95, 0.95))

text_behav_plot <- plot_grid(text_timecourse_plot, text_fst_shifts, 
                             rel_widths = c(0.9, 1),
                             labels = c("A"),
                             scale = c(0.95, 0.9))

save_plot(filename = here::here("paper/journal_submission/figures/figs_output/fig3_text_behav.png"), 
          text_behav_plot,
          ncol = 3,
          nrow = 2,
          base_aspect_ratio = 1)
```

### Model-based plots

```{r make text control chart}
# make control plot
text_ewma_vals <- d_ewma %>% 
  filter(rt <= 1, experiment == "text") %>% 
  aggregate_ewma

text_control_plot <- text_ewma_vals %>%
  plot_ewma_chart() +
  theme_minimal() +
  theme(panel.border = element_rect(fill = NA, color = "grey", size = 1),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 12),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12)) 
```

Ewma guessing plot.

```{r}
p_ewma_text <- d_ewma %>% 
  filter(rt <= 1.5, experiment == "text") %>% 
  group_by(subid, condition, guess) %>% 
  summarise(count = n()) %>% 
  mutate(prop.responding = round(count / sum(count), 2)) %>% 
  filter(guess == "response") %>% 
  ggplot(aes(x = fct_reorder(condition, prop.responding), y = prop.responding,
             fill = condition)) +
   ggbeeswarm::geom_quasirandom(shape = pt_shape, 
                               width = pt_width, 
                               color = pt_color, 
                               size = pt_size,
                               fill = "grey",
                               alpha = pt_alpha) +
  guides(fill=F) +
  lims(y = c(0,1)) +
  labs(x = "Condition", y = "Prop. Language-driven")  +
  scale_x_discrete(expand = c(0,1)) 

d_quantiles_ewma_text <- d_bda$ewma_guess_text %>% 
  mutate(face = bullseye + face,
         text = bullseye + text,
         `text-no-audio`= bullseye + text_no_audio) %>% 
  select(-text_no_audio) %>% 
  gather(key = condition, value = param_estimate, -sample_id) %>% 
  mutate(param_est_prob = logit_to_prob(param_estimate)) %>% 
  group_by(condition) %>% 
  summarise(ci_lower = hd(param_est_prob, q = 0.025),
            ci_upper = hd(param_est_prob, q = 0.975),
            prop.responding = hd(param_est_prob, q = 0.5))

p_ewma_text <- p_ewma_text +
  geom_pointrange(aes(ymax = ci_upper, ymin = ci_lower), 
                  data = d_quantiles_ewma_text,
                  color = "grey20",
                  shape = 15,
                  size = 0.7)
```

HDDM plot 

```{r density hddm plot}
p_hddm_text <- d_hddm %>% 
  filter(experiment == "text") %>%
  ggplot(aes(x = param_value, y = param_name, fill = condition)) +
  geom_density_ridges(scale = 0.7, rel_min_height = 0.005, alpha = 0.8) +
  ggthemes::scale_fill_ptol() +
  labs(x = "Parameter value", y = NULL, color = "") +
  scale_y_discrete(expand = c(0.2,0)) +
  theme(legend.position="top",
        legend.text = element_text(size = 9),
        legend.title = element_text(size = 10)) 

p_hddm_text
```

```{r forest hddm plot}
p_hddm_text <- d_hddm %>% 
  filter(experiment == "text") %>%
  group_by(param_name, condition) %>% 
  summarise(m = mean(param_value),
            lower = quantile(param_value, probs = 0.05),
            upper = quantile (param_value, probs = 0.95)) %>% 
  ggplot(aes(x = param_name, y = m, color = condition)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), size = 1,
                  position = position_dodge(width = .4)) +
  labs(y = "Parameter value", x = NULL, color = "Center stimulus: ") +
  lims(y =c(0.5,3.5))  +
  scale_color_brewer(palette="Dark2") +
  coord_flip() 

p_hddm_text
```


Put text model plots together.

```{r put model plots together}
text_ewma_hddm_plots <- plot_grid(p_ewma_text, p_hddm_text, ncol = 1, labels = c("B", "C"),
                                  scale = c(0.8, 0.8))

text_final_model_plot <- plot_grid(text_control_plot, text_ewma_hddm_plots, ncol = 2,
                                   rel_widths = c(1, 1.2), scale = c(0.95, 0.9),
                                   labels = "A")

save_plot(filename = here::here("paper/journal_submission/figures/figs_output/fig4_text_models.png"), 
          text_final_model_plot,
          ncol = 3,
          nrow = 2,
          base_aspect_ratio = 1)
```

