---
title: "Speed-Acc JEP: General Figure Visualization Code (Noise)"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb",
                      fig.path='figs/',echo=F, warning=F, cache=T, message=F, include =F,
                      sanitize = T)
```

# Set up 

This document contains the codebase for generating the plots for Study 3 in the paper, "An information-seeking account of children's eye movements during grounded signed and spoken language comprehension"

```{r load libraries}
source(here::here("R/helper_functions/libraries_and_functions.R"))
source(here::here("R/helper_functions/ewma_helper_funs.R"))
source(here::here("R/helper_functions/paper_helpers.R"))

# set data paths
data_path <- "data/3_final_merged_data/first_shifts/"
time_path <- "data/3_final_merged_data/timecourse/"
models_path <- "data/3_final_merged_data/bda_posterior_samples/"
ewma_path <- "data/3_final_merged_data/ewma_output/"
hddm_path <- "data/3_final_merged_data/hddm_output/"
```

```{r read data}
d_kids_noise <- read_csv(here::here(data_path, "speed_acc_child_noise_fstshift_tidy.csv")) %>% 
  select(-age)

d_adults <- read_csv(here::here(data_path, "speed_acc_adult_ng_fstshift_tidy.csv")) %>% 
  select(-age)

# merge datasets
d <- bind_rows(mutate(d_kids_noise, experiment = "kids_noise", age_category = "children"),
               mutate(d_adults, experiment = "adults_ng", age_category = "adults")) %>% 
  select(-resp_onset_type_fact, -subid_short) %>% 
  mutate(age_category = factor(age_category) %>% fct_rev(),
         gaze_condition = factor(gaze_condition) %>% fct_rev()) 

# test that we have the right number of rows after the merge (result should be TRUE)
nrow(d_kids_noise) + nrow(d_adults) == nrow(d)
```

```{r read ewma}
files <- dir(path = ewma_path, pattern = "*.csv") 
d_ewma <- files %>% purrr::map_df(read_ewma, path = ewma_path)
```

```{r read timecourse}
d_timecourse_adults <- read_csv(here::here(time_path, "speed_acc_adult_ng_timecourse_tidy.csv.gz"))
d_timecourse_adults %<>% mutate(age_code = "adults")

d_timecourse_kids <- read_csv(here::here(time_path, "speed_acc_child_noise_timecourse_tidy.csv.gz"))
d_timecourse_kids %<>% mutate(age_code = "children")

d_timecourse <- bind_rows(d_timecourse_adults, d_timecourse_kids)
```

```{r read model traces}
d_bda_noise <- readRDS(here::here(models_path, "speed-acc-noise-posterior-samples.rds"))
d_bda_ewma_noise <- readRDS(here::here(models_path, "speed-acc-noise-ewma-guess-posterior-samples.rds"))

# read hddm
d_hddm <- read_csv(here::here(hddm_path, "hddm_tidy.csv"))
```

# Plots for speech in background noise experiment

### Timecourse plots

Select plotting window and downsample the t.rel.noun time bins based on the sampling rate of the tracker. 

```{r}
samp_rate <- 30

d_time_filt <- d_timecourse %>% 
  filter(t.stim > 0, t.stim <= 9) %>% 
  filter(t.rel.noun >= 0, t.rel.noun <= 2.5) 

d_time_filt %<>% mutate(t.rel.noun = round(t.rel.noun * samp_rate) / samp_rate)
```

Summarise proportion looking at the participant level.

```{r}
# get number of trials looking at each gaze target for each time slice
ss.d <- d_time_filt %>% 
  group_by(subid, t.rel.noun, noise_condition, age_code) %>% 
  summarise(count = n()) %>% 
  ungroup() %>% 
  complete(nesting(subid, t.rel.noun, age_code), noise_condition,
           fill = list(count = 0)) %>% 
  mutate(subid = as.character(subid))

# get proportion looking by dividing the freq looking at each target by the total looking 
# derived in step 1 of this chunk
ss.d <- as.data.frame(xtabs(~ subid + t.rel.noun + target_looking + noise_condition + age_code, 
                            data = d_time_filt),
                      stringsAsFactors = F) %>% 
  mutate(t.rel.noun = as.numeric(t.rel.noun)) %>% 
  left_join(x = ss.d, y = ., by = c("subid", "t.rel.noun", "noise_condition", "age_code")) %>% 
  mutate(proportion_looking = Freq / count)
```

Summarise at the age group and condition level by computing means and bootsrapped CIs for each timepoint.

```{r, eval = F}
# nboot should be 500
nboot <- 500

ms_mean_iChart <- ss.d %>% 
  group_by(t.rel.noun, noise_condition, target_looking, age_code) %>% 
  langcog::multi_boot_standard(col = "proportion_looking", na.rm = T, nboot = nboot) %>% 
  filter(is.na(noise_condition) == F) 

write_csv(x = ms_mean_iChart, 
          path = here::here("paper/journal_submission/figures/noise_timecourse_graph_vals.csv"))
```

Make the timecourse plot.

```{r}
noise_time_gvs <- read_csv(here::here("paper/journal_submission/figures/noise_timecourse_graph_vals.csv"))

noise_time_gvs %<>% 
  filter(t.rel.noun <= 2.4, !(is.na(mean))) %>% 
  mutate(age_code = fct_relevel(age_code, "children", "adults"))

noise_timecourse_plot <- ggplot(aes(x = as.numeric(t.rel.noun), 
                                    y = mean, 
                                    color = noise_condition,
                                    linetype = target_looking), 
                                data = noise_time_gvs) + 
  geom_line(size = 1) +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.5) +
  xlab("Time from noun onset (sec)") +
  ylab("Proportion looking") +
  guides(linetype = F) +
  facet_wrap(~age_code, ncol = 2) +
  #ggthemes::scale_color_ptol() +
  scale_color_brewer(palette="Dark2") +
  geom_text_repel(
    data = filter(noise_time_gvs, t.rel.noun == max(t.rel.noun), 
                  noise_condition == "clear"),
    aes(label = target_looking),
    color = "grey40",
    size = 4,
    nudge_x = .1,
    segment.color = NA
  ) +
  lims(x = c(0, 2.8), 
       y = c(0,1)) 


noise_timecourse_plot
```

### First shifts plots

```{r filter noise experiment}
d_fst <- d %>% 
  filter(keep_runsheet %in% c("yes", "keep"), 
         keep_et == "include") %>% 
  filter(rt <= 1.5,
         response_onset_type == "noun",
         shift_start_location == "center") %>% 
  mutate(shift_acc_num = ifelse(shift_accuracy_clean == "correct", 1, 0),
         log_rt = log(rt))
```

Aggregate for accuracy and RT

```{r}
ss <- d_fst %>% 
  mutate(correct_num = ifelse(shift_accuracy == "correct", 1, 0)) %>% 
  group_by(noise_condition, subid, age_category) %>% 
  summarise(m_rt = median(rt),
            se_rt = sd(rt, na.rm = T) / sqrt(n()),
            m_acc = mean(correct_num),
            se_acc = sd(correct_num, na.rm = T) / sqrt(n()),
            n = n()) %>% 
  filter(n > 4)
```

Make within-subjects scatterplots

```{r}
# RT
means <- ss %>% 
  select(noise_condition, age_category, subid, m_rt) %>%
  spread(key=noise_condition, value=m_rt, sep = "_m_")

ses <- ss %>% 
  select(noise_condition, age_category, subid, se_rt) %>%
  spread(key=noise_condition, value= se_rt, sep = "_SE_")

sums <- left_join(means, ses) %>% 
  mutate(slower_cond = ifelse(noise_condition_m_clear > noise_condition_m_noise, "clear", "noise")) %>% 
  filter(!is.na(slower_cond))

lims <- c(0, 1.5)

ggplot(sums, aes(x=noise_condition_m_clear, y=noise_condition_m_noise, color = slower_cond)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin= noise_condition_m_noise - noise_condition_SE_noise, 
                    ymax = noise_condition_m_noise+noise_condition_SE_noise)) +
  geom_errorbarh(aes(xmin= noise_condition_m_clear - noise_condition_SE_clear, 
                     xmax = noise_condition_m_clear+noise_condition_SE_clear)) +
  geom_abline() +
  guides(color = F) +
  scale_color_brewer(palette = "Dark2") +
  facet_grid(.~age_category) +
  labs(x = "RT (sec) Clear", y = "RT (sec) Noise") +
  lims(x = lims, y = lims) +
  theme(aspect.ratio = 1)

# Accuracy
means <- ss %>% 
  select(noise_condition, age_category, subid, m_acc) %>%
  spread(key=noise_condition, value=m_acc, sep = "_m_")

ses <- ss %>% 
  select(noise_condition, age_category, subid, se_acc) %>%
  spread(key=noise_condition, value= se_acc, sep = "_SE_")

sums <- left_join(means, ses) %>% 
  mutate(slower_cond = ifelse(noise_condition_m_clear > noise_condition_m_noise, "clear", "noise")) %>% 
  filter(!is.na(slower_cond))

lims <- c(0, 1)

ggplot(sums, aes(x=noise_condition_m_clear, y=noise_condition_m_noise, color = slower_cond)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin= noise_condition_m_noise - noise_condition_SE_noise, 
                    ymax = noise_condition_m_noise+noise_condition_SE_noise)) +
  geom_errorbarh(aes(xmin= noise_condition_m_clear - noise_condition_SE_clear, 
                     xmax = noise_condition_m_clear+noise_condition_SE_clear)) +
  geom_abline() +
  guides(color = F) +
  scale_color_brewer(palette = "Dark2") +
  facet_grid(.~age_category) +
  labs(x = "Prop. Correct Clear", y = "Prop. Correct Noise") +
  lims(x = lims, y = lims) +
  theme(aspect.ratio = 1)
```

Make first shift accuracy plot.

```{r set global plot values}
pt_size <- 3
pt_alpha <- 0.5
pt_shape <- 21
pt_width <- 0.15
pt_color <- "black"
pt_fill <- "darkgrey"
nboot <- 500
```

```{r make noise acc plot}
p_acc <- ss %>% 
  filter(m_acc > 0) %>% 
  ggplot(aes(x = fct_relevel(noise_condition, "noise", after = 2), 
             y = m_acc, fill = noise_condition)) +
  ggbeeswarm::geom_quasirandom(shape = pt_shape, 
                               width = pt_width, 
                               color = pt_color, 
                               size = pt_size,
                               #fill = pt_fill,
                               alpha = pt_alpha) + 
  guides(fill = F) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  ggthemes::scale_fill_ptol() +
  labs(x = NULL, y = "Prop. Correct") +
  lims(y = c(0, 1)) +
  facet_wrap(~age_category, ncol = 1) 

# get model values
ms_acc_e1 <- d_bda_noise$acc_noise %>% 
  group_by(noise_condition, age_category) %>% 
  summarise(m_acc = mean(acc_prob_scale),
            hdi_lower = quantile(acc_prob_scale, probs = 0.025),
            hdi_upper = quantile(acc_prob_scale, probs = 0.975)) %>% 
  mutate_if(.predicate = is.numeric, .funs = round, digits = 2) %>% 
  mutate(age_category = factor(age_category) %>% fct_rev()) 

# add quantiles to plot
p_acc <- p_acc +
  geom_pointrange(aes(ymax = hdi_upper, ymin = hdi_lower), 
                  data = ms_acc_e1,
                  color = "grey20",
                  shape = 15,
                  size = 0.7)


# get pairwise diffs
diffs_df <- ss %>% 
  select(m_acc, subid, noise_condition, age_category) %>% 
  spread(noise_condition, m_acc) %>% 
  group_by(age_category) %>% 
  mutate(diff = noise - clear) 

ms_diffs <- diffs_df %>% 
  group_by(age_category) %>% 
  langcog::multi_boot_standard(col = "diff", na.rm = T, nboot = nboot) %>% 
  rename(diff = mean)

# now plot those differs
pairwise_diffs_plot_acc <- diffs_df %>% 
  mutate(title = "Pairwise contrast") %>%  # hack to get plots to line up nicely
  ggplot(aes(x = fct_rev(age_category), y = diff)) +
  geom_jitter(shape = pt_shape, 
              width = 0.1, 
              color = pt_color, 
              size = pt_size,
              fill = pt_fill,
              alpha = pt_alpha) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  data = ms_diffs,
                  shape = 15,
                  size = 0.7,
                  color = "grey20") +
  ylim(-0.45, 0.7) +
  labs(x = NULL, y = "Prop. correct difference") +
  coord_flip() +
  facet_wrap(~title) 

# put plots together
p_acc <- plot_grid(p_acc, pairwise_diffs_plot_acc, ncol = 2, rel_widths = c(0.9, 1),
                   scale = c(1, 0.85))
```

Make RT plot

```{r make text rt plot}
p_rt <- ss %>% 
  ggplot(aes(x = fct_reorder(noise_condition, m_rt, .fun = median), y = m_rt,
             fill = noise_condition)) +
  ggbeeswarm::geom_quasirandom(shape = pt_shape, 
                               width = pt_width + 0.1, 
                               color = pt_color, 
                               size = pt_size,
                               #fill = pt_fill,
                               alpha = pt_alpha) +  
  ylim(0, 1.3) +
  guides(fill = F) + 
  ggthemes::scale_fill_ptol() +
  labs(y = "RT (sec)", x = NULL) +
  coord_flip() +
  facet_wrap(~age_category, ncol = 1) 

# get model values
ms_rt_e1 <- d_bda_noise$rt_noise %>% 
  group_by(noise_condition, age_category) %>% 
  summarise(m_rt = mean(rt_ms_scale),
            hdi_lower = quantile(rt_ms_scale, probs = 0.025),
            hdi_upper = quantile(rt_ms_scale, probs = 0.975)) %>% 
  mutate_if(.predicate = is.numeric, .funs = round, digits = 2) %>% 
  mutate(age_category = factor(age_category) %>% fct_rev()) 

p_rt <- p_rt +
  geom_pointrange(aes(ymax = hdi_upper, ymin = hdi_lower), 
                  data = ms_rt_e1,
                  color = "grey20",
                  shape = 15,
                  size = 0.7)

# make pairwise differences plot
diffs_df <- ss %>% 
  select(m_rt, subid, noise_condition, age_category) %>% 
  spread(noise_condition, m_rt) %>% 
  group_by(age_category) %>% 
  mutate(diff = noise - clear) 

ms_diffs <- diffs_df %>% 
  group_by(age_category) %>% 
  langcog::multi_boot_standard(col = "diff", na.rm = T, nboot = nboot, 
                               empirical_function = "mean") %>% 
  rename(diff = mean)

pairwise_diffs_plot_rt <- diffs_df %>% 
  mutate(title = "Pairwise contrast") %>%  # hack to get plots to line up nicely
  ggplot(aes(x = fct_rev(age_category), y = diff)) +
  geom_jitter(shape = pt_shape, 
              width = 0.1, 
              color = pt_color, 
              size = pt_size,
              fill = pt_fill,
              alpha = pt_alpha) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  data = ms_diffs,
                  shape = 15,
                  size = 0.7,
                  color = "grey20") +
  ylim(-0.45, 0.7) +
  labs(x = NULL, y = "RT difference (sec)") +
  facet_wrap(~title) +
  coord_flip() 

p_rt <- plot_grid(p_rt, pairwise_diffs_plot_rt, ncol = 2, rel_widths = c(0.9, 1),
                  scale = c(1, 0.85))
```

### Merge behavioral plots and save

```{r}
noise_fst_shifts <- plot_grid(pairwise_diffs_plot_rt, pairwise_diffs_plot_acc, 
                              ncol = 1, 
                              rel_heights = c(0.95,1), 
                              labels = c("B", "C"),
                              scale = c(0.95, 0.95))

noise_behav_plot <- plot_grid(noise_timecourse_plot, noise_fst_shifts, 
                              rel_widths = c(1.5, 0.7),
                              labels = c("A"),
                              scale = c(0.95, 0.9))

save_plot(filename = here::here("paper/journal_submission/figures/figs_output/fig5_noise_behav.png"), 
          noise_behav_plot,
          ncol = 3,
          nrow = 1.5,
          base_aspect_ratio = 1)
```

## Model-based plots

### Control chart

```{r}
d_ewma %<>% filter(experiment %in% c("noise", "noise_gaze")) %>% 
  mutate(condition = ifelse(str_detect(condition, pattern = "noise"), "noise", "clear")) 
```


```{r make text control chart}
# make control plot adults
noise_ewma_vals_adults <- d_ewma %>% 
  filter(rt <= 1, age_code == "adult") %>% 
  aggregate_ewma

noise_control_plot_adults <- noise_ewma_vals_adults %>% plot_ewma_chart() +
  labs(title = "adults") +
  theme(strip.text = element_text(size = 18),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        panel.border = element_rect(color="black", fill=NA))

# make control plot kids
noise_ewma_vals_kids <- d_ewma %>% 
  filter(rt <= 1, age_code == "child") %>% 
  mutate(condition = ifelse(str_detect(condition, pattern = "noise"), "noise", "clear")) %>% 
  aggregate_ewma

noise_control_plot_kids <- noise_ewma_vals_kids %>% plot_ewma_chart() + 
  labs(title = "children") +
  theme(strip.text = element_text(size = 18),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        panel.border = element_rect(color="black", fill=NA))

## merge kids and adults plot
noise_control_chart <- plot_grid(noise_control_plot_kids, 
                                 noise_control_plot_adults, 
                                 ncol = 1) 
```

### EWMA guessing

```{r munge ewma data}
d_ewma %<>% 
  mutate(age_code = ifelse(str_detect(age_code, "child"), "children", "adults"),
         gaze_condition = ifelse(str_detect(condition, "gaze"), "gaze", 
                                 "straight_ahead"),
         noise_condition = ifelse(str_detect(condition, "noise"), "noise", "clear")) %>%
  filter(gaze_condition == "straight_ahead", rt <= 2) %>% 
  group_by(subid, noise_condition, age_code, guess) %>% 
  summarise(count = n()) %>% 
  mutate(prop.responding = round(count / sum(count), 2)) %>% 
  filter(guess == "response") 
```

Make the ewma guessing plot

```{r}
p_ewma_noise <- d_ewma %>%
  ungroup() %>%   
  mutate(age_code = fct_rev(age_code)) %>% 
  ggplot(aes(x = noise_condition, y = prop.responding, fill = noise_condition)) +
  ggbeeswarm::geom_quasirandom(shape = pt_shape, 
                               width = pt_width, 
                               color = pt_color, 
                               size = pt_size,
                               #fill = "grey",
                               alpha = pt_alpha) +
  lims(y = c(0,1)) +
  guides(fill = F, alpha = F)+
  #ggthemes::scale_fill_ptol() +
  scale_fill_brewer(palette="Dark2") +
  scale_x_discrete(expand = c(0,0.8), drop = FALSE) +
  facet_wrap(~age_code) +
  labs(x = NULL, y = "Prop. Language-driven", fill = "Processing context:") 

d_quantiles_ewma_noise <- d_bda_noise$ewma_guess_noise %>% 
  rename(age_code = age_category) %>% 
  group_by(noise_condition, age_code) %>% 
  summarise(ci_lower = hd(param_est, q = 0.025),
            ci_upper = hd(param_est, q = 0.975),
            prop.responding = hd(param_est, q = 0.5)) %>% 
  mutate(age_code = fct_rev(age_code)) 

# add quantiles to plot
p_ewma_noise <- p_ewma_noise +
  geom_pointrange(aes(x = noise_condition, y = prop.responding,
                      ymax = ci_upper, ymin = ci_lower,
                      group = noise_condition),
                  data = d_quantiles_ewma_noise,
                  position = position_dodge(width = 0.8),
                  inherit.aes = F,
                  color = "grey20",
                  shape = 15,
                  fatten = 3.5,
                  size = 1)

p_ewma_noise
```

### HDDM parameter estimates

```{r ridges plot hddm}
p_hddm_noise <- d_hddm %>% 
  filter(experiment %in% c("noise_gaze", "noise"),
         condition %in% c("gaze_noise", "straight_ahead_clear",
                          "clear", "noise")) %>%
  mutate(condition = ifelse(str_detect(condition, "noise"), "noise", "clear"),
         age_code = factor(age_code, levels = c("children", "adults"))) %>% 
  ggplot(aes(x = param_value, y = param_name, fill = condition, 
             alpha = age_code, linetype = age_code)) +
  geom_density_ridges(scale = 0.8, rel_min_height = 0.005, size = 1) + 
  labs(x = "Parameter value", y = NULL, color = "",
       fill = "Condition:",
       linetype = "Age group:") +
  guides(alpha = F) +
  scale_y_discrete(expand = c(0.2,0)) +
  scale_alpha_manual(values = c(0.9, 0.6)) + 
  ggthemes::scale_fill_ptol() 

p_hddm_noise
```

```{r dot plot hddm}
p_hddm_noise <- d_hddm %>% 
  filter(experiment %in% c("noise_gaze", "noise"),
         condition %in% c("gaze_noise", "straight_ahead_clear",
                          "clear", "noise")) %>%
  mutate(condition = ifelse(str_detect(condition, "noise"), "noise", "clear"),
         age_code = factor(age_code, levels = c("children", "adults")),
         param_name = fct_rev(param_name)) %>% 
  group_by(param_name, condition, age_code) %>% 
  summarise(m = mean(param_value),
            lower = quantile(param_value, probs = 0.05),
            upper = quantile (param_value, probs = 0.95)) %>% 
  ggplot(aes(x = condition, y = m, color = condition)) +
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                  size = 1,
                  fatten = 2,
                  position = position_dodge(width = .4)) +
  labs(y = "Parameter value", x = NULL, color = "Center stimulus: ") +
  guides(color = F)+
  #ggthemes::scale_color_ptol() +
  scale_color_brewer(palette="Dark2") +
  lims(y = c(0.2,2.2)) +
  facet_grid(age_code~param_name, scales = "free") +
  coord_flip() 

p_hddm_noise
```


### Merge and save model plots

```{r}
noise_ewma_hddm_plots <- plot_grid(p_ewma_noise, p_hddm_noise, 
                                   rel_heights = c(0.8,1), 
                                   ncol = 2, 
                                   labels = c("A", "B"), 
                                   scale = c(0.95, 0.9))

# noise_final_model_plot <- plot_grid(noise_control_chart, noise_ewma_hddm_plots, 
#                                     ncol = 2,
#                                     rel_widths = c(1, 1), 
#                                     scale = c(0.9, 0.9),
#                                     labels = "A")

save_plot(filename = here::here("paper/journal_submission/figures/figs_output/fig6_noise_models.png"), 
          noise_ewma_hddm_plots,
          ncol = 3,
          nrow = 1,
          base_aspect_ratio = 1)
```

