---
title: "Speed-Acc Power Analysis"
author: "Kyle MacDonald"
output: html_document
---

### Set up

```{r chunk_options, echo = F}
rm(list=ls()) # code to clear workspace

knitr::opts_chunk$set(warning=F, message=F, sanitize = T, 
                      fig.height=5, fig.width=8, echo=T, cache = F)

source("../../helper_functions/libraries_and_functions.R")
library(pwr)
```

### Load data

To get a rough sample size estimate for the speed-acc noise and gaze manipulations I am using the difference in Accuracy and RT between the Object and Face conditions from Experiment 1. 

```{r}
df <- read.csv("../../../data/3_final_merged_data/speed-acc-ss-df.csv", 
               check.names=F, stringsAsFactors=F) 

df %<>% 
  mutate(stimuli = ifelse(stimuli == "V1" | stimuli == "V2", "ASL", 
                          ifelse(stimuli == "Trio", "Object", 
                                 ifelse(stimuli == "Bull", "Bullseye",
                                        stimuli))),
         stimuli = factor(stimuli, levels = c("ASL", "Face", "Object", "Bullseye")))
```


### Compute effect size for the accuracy and RT difference between Object and Face conditions

$$ d = \frac{\bar{x}_1 - \bar{x}_2}{s} $$

s is defined as the pooled standard deviation:

$$ s = \sqrt{\frac{s^2_1 + s^2_2}{n_1 + n_2 - 2}} $$

and variance for one of the groups is defined as:

$$ s^2 = \frac{1}{n-1}\sum{(x_{1,i} - \bar{x}_1)^2}$$

```{r}
d_effsize <-  df %>% 
  filter(stimuli %in% c("Object", "Face"), age_code == "child", 
         trial_type != "no_shift") %>% 
  group_by(stimuli, Sub.Num) %>% 
  summarise(ss_m = mean(correct, na.rm = T))

cohen.d(filter(d_effsize, stimuli == "Object")$ss_m, filter(d_effsize, stimuli == "Face")$ss_m, 
        hedges.correction = T) 
```

```{r}
rt_effsize <-  df %>% 
  filter(stimuli %in% c("Object", "Face"), age_code == "child", 
         trial_type != "no_shift", correct == 1) %>% 
  group_by(stimuli, Sub.Num) %>% 
  summarise(ss_m = mean(RT_sec))

cohen.d(filter(rt_effsize, stimuli == "Object")$ss_m, filter(rt_effsize, stimuli == "Face")$ss_m,
        hedges.correction = T)
```

```{r define constants}
acc_cohd <- -0.5085439
rt_cohd <- -1.64498
sig_level <- .05
power <- 0.90
```


### Estimate sample size to achieve 90% power

From http://www.statmethods.net/stats/power.html

The following four quantities have an intimate relationship:

* sample size
* effect size
* significance level = P(Type I error) = probability of finding an effect that is not there
* power = 1 - P(Type II error) = probability of finding an effect that is there

Given any three, we can determine the fourth. With those quantities, we can now compute the sample size we would need to have 80% power to detect an effect of that size.

```{r}
## Accuracy 
pwr.t.test(d = acc_cohd, sig.level = sig_level, power = power, type = c("paired"))
```

```{r}
## Accuracy 
pwr.t.test(d = rt_cohd, sig.level = sig_level, power = power, type = c("paired"))
```

So to achieve 90% power to detect the smaller Accuracy effect, we would need to run 43 participants in both the Gaze and Noise experiments.