---
title: "Speed-Acc Child Gaze First-shift Analysis"
output: html_document
---

## Set up 
 
```{r chunk_options, echo = F}
# code to clear workspace
rm(list=ls()) 

# set some global options
knitr::opts_chunk$set(warning=F, message=F, sanitize = T, 
                      fig.height=4, fig.width=8, echo=T, cache = F)
```

```{r}
# read in personal library of helper functions
source("../../helper_functions/libraries_and_functions.R")
```

## Load data

```{r}
d <- read_csv("../../../data/3_final_merged_data/first_shifts/speed_acc_child_gaze_fstshift_tidy.csv")
```

## Check the data

How many participants in the dataset?  

```{r}
d %>% select(subid_short) %>% unique() %>% count
```

How many trials do we have for each participant in each condition? 

```{r, eval = F}
d %>% 
  group_by(subid, gaze_condition) %>% 
  summarise(n_trials = n()) %>% 
  kable()
```

## Explore data via visualization

What does the distribution of age in the sample look like? 

```{r, fig.width=4}
d %>% 
  select(subid_short, age_group) %>% 
  unique() %>% 
  ggplot(aes(x = age_group)) +
  geom_histogram()
```

What about Reaction Times (RT)?

```{r, fig.width=6}
ggplot(aes(x = rt), data = d) +
  geom_histogram()
```

What about Accuracy? 

```{r, fig.width=5}
d %>% 
  filter(shift_type %in% c("C_T", "C_D")) %>% 
  ggplot(aes(x = shift_accuracy)) +
  geom_bar()
```

## Filter the data

Next, let's remove extreme RTs. 

```{r}
d.filt <- d %>% 
  filter(rt <= 5,
    keep_et == "include",
    keep_runsheet == "keep")
```

### Visualize Accuracy

What is the overall accuracy of first shifts?

```{r}
ss <- d.filt %>% 
  filter(!is.na(shift_accuracy_clean),
         shift_start_location == "center",
         rt <= 1.5) %>% 
  group_by(gaze_condition, subid, shift_accuracy_clean, age_group, block) %>% 
  summarise(n = n()) %>% 
  group_by(subid, gaze_condition, age_group) %>% 
  mutate(total_trials = sum(n),
         prop = round(n / total_trials, 2)) 
```

Now make a boxplot of the accuracy data for each condition. Note that we have to first filter out the proprotion "incorrect" rows, so we are only seeing the proprotion correct data.

```{r}
acc_boxplot <- ss %>% 
  filter(shift_accuracy_clean == "correct") %>% 
  ggplot(aes(x = gaze_condition, y = prop)) +
  geom_boxplot(width = 0.2, fill = "dodgerblue", notch = T) +
  #geom_jitter(width = 0.05, alpha = 0.3) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  labs(x = "Condition", y = "Prop. Correct") 
```

Make accuracy by block plot.

```{r}
acc_block <- ss %>% 
  filter(shift_accuracy_clean == "correct") %>% 
  ggplot(aes(x = gaze_condition, y = prop)) +
  geom_boxplot(width = 0.2, fill = "dodgerblue") +
  #geom_jitter(width = 0.05, alpha = 0.3) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  labs(x = "Condition", y = "Prop. Correct") +
  facet_wrap(~block)
```

### Visualize Reaction Time

What is the overall RT for kids in the experiment? 

```{r}
rt_boxplot <- d.filt %>% 
  filter(!is.na(shift_accuracy_clean), 
         shift_type %in% c("C_T", "C_D"),
         rt <= 1.5) %>% 
  group_by(subid, gaze_condition) %>% 
  summarise(m_rt = median(rt)) %>% 
  ggplot(aes(x = gaze_condition, y = m_rt)) + 
  geom_boxplot(width = 0.2, fill = "darkorange", notch = T) +
  ylim(0,1) +
  labs(x = "Condition", y = "RT (sec)") 
```

Make RT by block plot.

```{r}
rt_block <- d.filt %>% 
  filter(!is.na(shift_accuracy_clean), 
         shift_type %in% c("C_T", "C_D"),
         rt <= 1.5) %>% 
  group_by(subid, gaze_condition, block) %>% 
  summarise(m_rt = median(rt)) %>% 
  ggplot(aes(x = gaze_condition, y = m_rt)) + 
  geom_boxplot(width = 0.2, fill = "darkorange") +
 # geom_jitter(width = 0.05, alpha = 0.3) + 
  ylim(0, 1) +
  labs(x = "Condition", y = "RT (sec)") +
  facet_wrap(~block)
```

### Plot RT and Accuracy together

```{r}
cowplot::plot_grid(rt_boxplot, acc_boxplot)
```

### Plot RT and Accurcy block effects

```{r}
cowplot::plot_grid(rt_block, acc_block)
```

## Predictions with fake data

```{r}
prediction <- c("speed accuracy tradeoff", "speed accuracy tradeoff", "language cue dominates", "language cue dominates", "gaze cue dominates", "gaze cue dominates")
condition <- c("gaze", "no_gaze", "gaze", "no_gaze", "gaze", "no_gaze")
reaction_time <- c(0.9, 0.6, 0.6, 0.6, 1.4, 0.6)
accuracy <- c(0.9, 0.55, 0.55, 0.55, 0.95, 0.55)

fake_df <- data.frame(prediction, condition, reaction_time, accuracy)

fake_df %<>% gather(key = measure, value = response, reaction_time:accuracy)
```

Now plot the predictions

```{r}
fake_df %>% 
  ggplot(aes(x = condition, y = response, fill = prediction)) +
  geom_bar(stat = "identity", width = 0.3) +
  facet_grid(measure~prediction, scales = "free_y") +
  guides(fill = F) +
  scale_fill_manual(values = c("dodgerblue", "darkred", "darkorange")) 
```

