---
title: "Speed-Acc Noise Gaze Analysis"
author: "Kyle MacDonald"
output: html_document
---

## Set up 

Here are some helpful links for understanding the workflow for analyzing data in R Markdown (what you're doing in this document!):

 * [Scripts](http://r4ds.had.co.nz/workflow-scripts.html)
 * An R Markdown [guide](https://docs.google.com/document/d/1ajv1VJqEheVws93tnzH-K7145vBKtwD3Az5pg3faRdw/edit?usp=sharing) that I wrote for the lab
 
```{r chunk_options, echo = F}
# code to clear workspace
rm(list=ls()) 

# set some global options
knitr::opts_chunk$set(warning=F, message=F, sanitize = T, 
                      fig.height=5, fig.width=8, echo=T, cache = F)
```

```{r}
# read in personal library of helper functions
source("../../helper_functions/libraries_and_functions.R")
```

## Load data

Section 11.2 from [this](http://r4ds.had.co.nz/data-import.html) chapter on data importing is great.

**KM note**: this way of reading the file will work, but it only will work on your computer since this part of the path [~/Desktop/Research/] is specific to where you saved the data. The solution is to use a relative path like I've done here. You can check out this [video](https://www.youtube.com/watch?v=fe6GA200dks) for more background.

```{r}
# read in the data using a relative path that starts from the analysis file directory
d <- read_csv("../../../data/3_final_merged_data/first_shifts/speed_acc_adult_ng_fstshift_tidy.csv")
```

## Check the data

The goal of this section is to make sure the data match our expectations, or in other words, we are "testing" our data. Usually this involves comparing a known value to the number actually in the data set. For example, I know how I ran 20 participants, do I have 20 unique participant IDs?

[This](http://r4ds.had.co.nz/transform.html) chapter from the book **R for Data Science** is a good reference for writing code to manipulate data to do data "sanity" checks.

How many participants in the dataset?  

```{r}
d %>% select(subid) %>% unique() %>% count()
```

How many trials do we have for each participant?

```{r}
d %>% 
  group_by(subid) %>% 
  select()
```

Looks like we need to create a single variable that stores information about both the noise and gaze condition. 

```{r}
d %<>% mutate(condition_long = paste(gaze_condition, noise_condition, sep = "_"))
```

**KM note**: Now we can see how many trials are in each condition.

```{r}
d %>% 
  filter(response_onset_type == "noun") %>% 
  group_by(subid, condition_long) %>% 
  summarise(n = n()) %>% 
  kable()
```

TODO: Check out what's going on with #8

This looks like a data merging issue where #8's data. Not sure what's going on?

## Explore data via visualization

[This](http://r4ds.had.co.nz/data-visualisation.html) is a great book chapter on data visualization using the ggplot2 R package

### Visualize data distributions

What about Reaction Times (RT)?

```{r}
ggplot(d, aes(x = rt, color = condition_long)) +
  geom_freqpoly(alpha = 1, size = 1) +
  facet_grid(~response_onset_type) +
  theme_bw()
```

What about Accuracy? 

```{r}
d %>% 
  filter(response_onset_type == "sentence", shift_type %in% c("C_T", "C_D")) %>% 
  ggplot() +
  geom_bar(mapping = aes(x = subid, fill = shift_accuracy)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## filter the data

Let's filter out the participants who was not a native speaker of English

```{r}
d.filt <- d %>% filter(!(subid %in% c("speed_acc_adult_ng_1", "speed_acc_adult_ng_8")), 
                       response_onset_type == "center.fixation")
```

Next, let's remove extreme RTs. 

```{r}
d.filt %<>% filter(rt <= 5)
```

### Visualize Accuracy

What is the overall accuracy of first shifts?

```{r}
ggplot(d.filt) + 
  geom_bar(mapping = aes(x = shift_accuracy))
```

Let's visualize accuracy collapsing across the gaze and noise conditions. First we are going to summarise to get a proportion correct for each participant and condition. Then we aggregate again to get an overall proportion correct for each condition. 

```{r}
# aggregate accuracy at the participant level
ss.acc <- d.filt %>% 
  filter(!is.na(shift_accuracy),
        shift_type %in% c("C_T", "C_D")) %>% 
        # str_detect(condition_long, "no_noise")) 
  group_by(condition_long, subid, shift_accuracy) %>% 
  summarise(n = n()) %>% 
  group_by(subid, condition_long) %>% 
  mutate(total_trials = sum(n),
         prop = round(n / total_trials, 2)) 
```

Now make a boxplot of the accuracy data for each condition. Note that we have to first filter out the proprotion "incorrect" rows, so we are only seeing the proprotion correct data.

```{r}
acc_boxplot <- ss.acc %>% 
  filter(shift_accuracy == "correct") %>% 
  ggplot(aes(x = condition_long, y = prop)) +
  geom_boxplot(width = 0.5, fill = "dodgerblue") +
  geom_jitter(width = 0.05, alpha = 0.3) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  labs(x = "Condition", y = "Prop. Correct") +
  theme(text = element_text(size = 18)) +
  ylim(0,1)
```

### Visualize Reaction Time

RT Boxplot

```{r}
ss.rt <- d.filt %>% 
  filter(!is.na(shift_accuracy),
         shift_type %in% c("C_T", "C_D"),
         str_detect(condition_long, "no_noise")) %>% 
  group_by(gaze_condition, subid) %>% 
  summarise(m_rt = mean(rt))
```

```{r}
rt_boxplot <- ss.rt %>% 
  ggplot(aes(x = gaze_condition, y = m_rt)) +
  geom_boxplot(width = 0.5, fill = "#de2d26") +
  geom_jitter(width = 0.05, alpha = 0.3) + 
  ylim(0,1) +
  labs(x = "Condition", y = "RT (sec)") +
  theme(text = element_text(size = 18))
```

```{r}
cowplot::plot_grid(rt_boxplot, acc_boxplot)
```


## RT Distributions

```{r}
acc_colors <- c("grey10", "black")
fill_vals <- c("grey90", "darkviolet")

p <- d %>% 
  filter(is.na(rt) == F,
         rt <= 4,
         str_detect(condition_long, "no_noise")) %>% 
  ggplot(aes(x = forcats::fct_rev(gaze_condition), y = rt)) +
  ggbeeswarm::geom_quasirandom(shape = 21, fill = "black", color = "black") + 
  labs(y = "RT (sec)", x = NULL) +
  theme_bw() +
  theme(legend.position = "right") + 
  theme(axis.title.x = element_text(size = 18, 
                                    face = "bold"), 
        axis.title.y = element_text(size = 18,
                                    face = "bold"), axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 18)) +
  coord_flip()

p
```


## Statistical models

We can talk more about this aspect of the anlaysis once you made some progress on data viz. 


