---
title: "Speed-acc Trio Behavioral Analyses"
author: "Kyle MacDonald"
output: html_document
---

## Set up

There are 4 different types of center fixations in this dataset:

1. ASL (27 kids: 18-54m, median age = 27 months): human signing
2. Face (22 kids: 26m): human face talking
3. Trio (18 kids at 26m and 22 kids at 36m): static images of real world objects, e.g., cats
4. Bull (22 kids at 26m): different static "bullseyes"

```{r chunk_options, echo = F}
rm(list=ls()) # code to clear workspace

knitr::opts_chunk$set(warning=F, message=F, sanitize = T, 
                      fig.height=5, fig.width=8, echo=T, cache = F)

source("../../helper_functions/libraries_and_functions.R")
```

Load data and do some minor clean up of condition names.

```{r}
df <- read.csv("../../../data/3_final_merged_data/speed-acc-participant-level-df.csv", 
               check.names=F, stringsAsFactors=F) 

df %<>% 
  mutate(stimuli = ifelse(stimuli == "V1" | stimuli == "V2", "ASL", 
                          ifelse(stimuli == "Trio", "Object", 
                                 ifelse(stimuli == "Bull", "Bullseye",
                                        stimuli))),
         stimuli = factor(stimuli, levels = c("ASL", "Face", "Object", "Bullseye")))
```

## Descriptive information

How many participants in each stimuli set and language modality? `Age_code_m` is a hacky way to track the different age groups that saw the Trio stimuli.

```{r}
df %>% 
  select(Sub.Num, language_modality, age_code, stimuli) %>% 
  unique() %>% 
  group_by(language_modality, age_code, stimuli) %>% 
  dplyr::summarise(count = n()) %>% 
  knitr::kable()
```

What are the age distributions across language modalities?

```{r}
df %>% 
  filter(age_code == "child") %>% 
  select(Sub.Num, language_modality, age_code, stimuli, age_years) %>% 
  unique() %>%
  ggplot(aes(age_years, color = stimuli)) +
  geom_freqpoly() +
  scale_fill_solarized() +
  facet_grid(.~language_modality)
```

ASL group has wide range of ages; whereas the spoken language kids are tightly clustered around 2 and 3 years of age.

## Accuracy analysis

First we need to get proportion correct for each participant in each age group and language modality.

```{r}
ss_prop <- df %>% 
  group_by(Sub.Num, age_code, Months, language_modality, 
           stimuli, hearing_status_participant) %>% 
  filter(trial_type != "no_shift") %>% 
  summarise(mean_correct = mean(correct))

ss_prop <- df %>% 
  group_by(Sub.Num, age_code, Months, language_modality, stimuli, correct, 
           hearing_status_participant) %>%
  filter(trial_type != "no_shift") %>% 
  summarise(mean_rt = median(RT)) %>% 
  left_join(ss_prop)
```

Plot.

```{r boxplot}
ggplot(aes(x = stimuli, y = mean_correct, fill = language_modality), 
       data = filter(ss_prop, age_code == "child", correct == 1)) +
  geom_boxplot(outlier.colour = "red", width = 0.3) +
  geom_jitter(width = 0.1, alpha = 0.35) +
  geom_hline(yintercept = 0.5, lty = "dashed") +
  ylim(0,1) +
  xlab(NULL) +
  ylab("Mean Accuracy") +
  scale_fill_solarized() +
  theme(text = element_text(size=16)) +
  guides(fill = F) +
  ggtitle("First shift accuracy")
```

When we plot the average proprotion of correct shifting, we see that the ASL group was the most accurate, followed by Face, and then Trio and Bull.

Model the accuracy difference between ASL and Face:

```{r}
m1 <- glmer(correct ~ stimuli + (1|Sub.Num), 
            data = filter(df, age_code == "child", stimuli %in% c("ASL", "Face")),
            family = "binomial")

m1 %>% 
  broom::tidy() %>% 
  filter(group == "fixed") %>%
  select(-group) %>% 
  knitr::kable(digits = 3)
```

Compute effect size for the accuracy difference between ASL and Face:

$$ d = \frac{\bar{x}_1 - \bar{x}_2}{s} $$

s is defined as the pooled standard deviation:

$$ s = \sqrt{\frac{s^2_1 + s^2_2}{n_1 + n_2 - 2}} $$

and variance for one of the groups is defined as:

$$ s^2 = \frac{1}{n-1}\sum{(x_{1,i} - \bar{x}_1)^2}$$

```{r}
d_effsize <-  df %>% 
  filter(stimuli %in% c("ASL", "Face"), age_code == "child", 
         trial_type != "no_shift") %>% 
  group_by(stimuli, Sub.Num) %>% 
  summarise(ss_m = mean(correct))

cohen.d(filter(d_effsize, stimuli == "ASL")$ss_m, 
         filter(d_effsize, stimuli == "Face")$ss_m)
```

## RT analysis

Get medians and CIs for correct/inccorect shifts for each stimuli set and language modality 

```{r}
ms_rt <- ss_prop %>%
  filter(age_code == "child") %>% 
  group_by(language_modality, age_code, stimuli, correct) %>% 
  multi_boot_standard(column = "mean_rt", na.rm = T, empirical_function = "median")
```

RT boxplot

```{r rt boxplot}
ss_prop$stimuli <- factor(ss_prop$stimuli, 
                          levels = c("Bullseye", "Object", "Face", "ASL"))

ggplot(aes(x = stimuli, y = mean_rt, fill = language_modality), 
       data = filter(ss_prop, age_code == "child", correct == 1)) + 
  geom_boxplot(outlier.colour = "red") +
  geom_jitter(width = 0.2, alpha = 0.35) +
  scale_fill_solarized() +
  guides(fill = F) + 
  theme(text = element_text(size=16)) +
  xlab(NULL) +
  ylab("Median RT") +
  coord_flip() +
  ggtitle("Reaction Time")
```

Plot RTs for correct/incorrect tirals

```{r}
ss_prop$stimuli <- factor(ss_prop$stimuli, 
                          levels = c("Bullseye", "Object", "Face", "ASL"))

ggplot(aes(x = stimuli, y = (mean_rt / 1000), fill = as.factor(correct)), 
       data = filter(ss_prop, age_code == "child")) + 
  geom_boxplot(outlier.colour = "red") +
  scale_fill_solarized() +
  guides(fill = F) + 
  theme(text = element_text(size=16)) +
  xlab(NULL) +
  ylab("Median RT") +
  coord_flip() +
  ggtitle("Reaction Time")
```

We see some evidence of speed accuracy tradeoffs in the ASL, Face, and Bull conditions, but not in the Trio condition. Why do medians look so much better than means? 

Compute effect size for RT difference on correct shifts.

```{r}
m_rt <- lmer(RT_sec ~ stimuli + (1|Sub.Num), 
            data = filter(df, age_code == "child", 
                          stimuli %in% c("ASL", "Face"),
                          correct == 1))
```

```{r}
rt_effsize <-  df %>% 
  filter(stimuli %in% c("ASL", "Face"), age_code == "child", 
         trial_type != "no_shift", correct == 1) %>% 
  group_by(stimuli, Sub.Num) %>% 
  summarise(ss_m = median(RT_sec))

cohen.d(filter(rt_effsize, stimuli == "ASL")$ss_m,
        filter(rt_effsize, stimuli == "Face")$ss_m)
```
