---
title: "Speed-Acc-Child Noise first shift analysis"
output: html_document
---

## Set up 

```{r chunk_options, echo = F}
# set some global options
knitr::opts_chunk$set(warning=F, message=F, sanitize = T, 
                      fig.height=4, fig.width=8, echo=T, cache = F)
```

read in personal library of helper functions

```{r}
library(here)
source(here::here("R/helper_functions/libraries_and_functions.R"))
data_path <- "data/3_final_merged_data/first_shifts/"
theme_set(ggthemes::theme_few())
```

## Load data

```{r}
d <- read_csv(here::here(data_path, "speed_acc_child_noise_fstshift_tidy.csv")) 
```

## Check the data

How many participants in the dataset?  

```{r}
d %>% distinct(subid_short) %>% count() %>% kable()
```

How many trials do we have for each participant?

```{r, eval = F}
d %>% 
  select(subid_short, tr.num) %>% 
  unique() %>% 
  group_by(subid_short) %>%
  count() %>% 
  kable()
```

Not every participant has the same number of trials, but no participant has more than 32 trials, which is good.

How many trials does each participoant have in each condition? 

```{r, eval = F}
trials_df <- d %>% 
  filter(!(is.na(rt))) %>% 
  select(subid_short, tr.num, noise_condition) %>% 
  unique() %>% 
  group_by(subid_short, noise_condition) %>%
  count() 

# add this information to the rest of the data
d %<>% left_join(., trials_df, by = c("subid_short", "noise_condition"))

trials_df %>% kable()
```

What's the average number of trials for each condition?

```{r}
d %>% 
  filter(!(is.na(rt))) %>% 
  select(subid_short, noise_condition, tr.num) %>% 
  unique() %>% 
  group_by(subid_short, noise_condition) %>% 
  summarise(n = n()) %>% 
  group_by(noise_condition) %>% 
  summarise(avg_trials = mean(n) %>% round(digits = 2))
```

Let's visualize it just to be sure there's no difference in attrition.

```{r}
d %>% 
  filter(!(is.na(rt))) %>% 
  select(subid_short, noise_condition, tr.num) %>% 
  unique() %>% 
  group_by(subid_short, noise_condition) %>% 
  summarise(n = n()) %>% 
  ggplot(aes(x = n, color = noise_condition)) +
  geom_freqpoly() +
  geom_vline(xintercept = 8, linetype = "dashed")
```

The distribution of trials completed looks pretty similar across conditions, which is nice. 

## Data filtering

Remove shifts that do not start at center, participant exclusions, and extreme RTs

```{r}
d.analysis <- d %>% 
  filter(!(is.na(shift_accuracy_clean)),
         response_onset_type == "noun",
         keep_et == "include",
         keep_runsheet == "keep",
         rt <= 1.5) 
```

## Explore data via visualization

What does the distribution of age in the sample look like? 

```{r}
d.analysis %>% 
  select(subid_short, age_group) %>% 
  unique() %>% 
  ggplot(aes(x = as.factor(age_group))) +
  geom_histogram(stat = 'count')
```

Plot the distribution of Reaction Times (RT)

```{r}
d.analysis %>% 
  filter(shift_start_location == "center") %>% 
  ggplot() + 
  geom_density(mapping = aes(x = rt, fill = noise_condition), 
               alpha = 0.5, binwidth = 0.05, position = "identity", 
               adjust = 2) +
  facet_grid(shift_accuracy_clean~block)
```

## Aggregated visualizations

Aggregate RT

```{r}
ss.rt <- d.analysis %>% 
  filter(shift_start_location == "center") %>% 
  group_by(subid_short, noise_condition, shift_accuracy_clean, block) %>% 
  summarise(m_rt = median(rt, na.rm = T)) 
```

Make RT boxplot.

```{r}
rt_boxplot <- ss.rt %>% 
  filter(block == "block_1") %>% 
  ggplot(aes(x = noise_condition, y = m_rt, fill = shift_accuracy_clean)) + 
  geom_boxplot(width = 0.2, notch = F, outlier.colour = "white") +
  ylim(0, 1) +
  scale_x_discrete(expand = c(0,1)) +
  scale_fill_manual(values = c("darkorange", "dodgerblue")) +
  theme_classic() +
  theme(legend.position=c(0.35,0.9),
        legend.direction="horizontal", 
        legend.background = element_rect(fill=alpha('white', 0.4)),
        text = element_text(size = 12)) +
  labs(x = "Condition", y = "RT (sec)", fill = NULL)  
   

rt_boxplot
```

Make plot for RT block effects

```{r}
rt_block <- ss.rt %>% 
  ggplot(aes(x = noise_condition, y = m_rt, fill = shift_accuracy_clean)) + 
  geom_boxplot(width = 0.3) +
  ylim(0,1) +
  labs(x = "Condition", y = "RT (sec)")  +
  facet_wrap(~block) +
  langcog::scale_fill_solarized() +
  theme(legend.position = "top")
```

### Aggregate Accuracy

```{r}
ss.acc <- d.analysis %>% 
  filter(shift_start_location == "center") %>% 
  group_by(noise_condition, subid_short, shift_accuracy_clean) %>% 
  summarise(n = n()) %>% 
  group_by(subid_short, noise_condition) %>% 
  mutate(total_trials = sum(n),
         prop = round(n / total_trials, 2)) 
```

Now make accuracy boxplot

```{r}
acc_boxplot <- ss.acc %>% 
  filter(shift_accuracy_clean == "correct") %>% 
  ggplot() + 
  geom_boxplot(mapping = aes(x = noise_condition, y = prop), 
               width = 0.2,
               fill = "darkgrey",
               notch = F) +
  scale_x_discrete(expand = c(0,1)) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  labs(x = "Condition", y = "Prop. Correct") +
  ylim(0.2,1) +
  theme_classic() +
  theme(text = element_text(size = 12))
```


```{r}
acc_block <- ss.acc %>% 
  filter(shift_accuracy_clean == "correct") %>% 
  ggplot() + 
  geom_boxplot(mapping = aes(x = noise_condition, y = prop), 
               width = 0.2,
               fill = "dodgerblue") +
  scale_y_continuous(limits=c(0,1)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  labs(x = "Condition", y = "Prop. Correct") +
  facet_wrap(~block) 
```

### Plot Acc and RT together

```{r}
cowplot::plot_grid(rt_boxplot, acc_boxplot, ncol = 1)
```

### Plot Block effects

```{r}
cowplot::plot_grid(rt_block, acc_block)
```

## Learning effects

```{r}
n_trials_block <- 16
d.analysis %<>% mutate(tr.num.block = ifelse(block == "block_1", 
                                             tr.num, 
                                             tr.num - n_trials_block))
```

Summarise and plot the change in RT over the course of a block.

```{r}
d.analysis %>% 
  filter(shift_start_location == "center") %>% 
  mutate(tr.num.bin = cut(tr.num.block, breaks = 3)) %>% 
  group_by(subid_short, noise_condition, shift_accuracy_clean, tr.num.bin, block) %>% 
  summarise(m_rt = median(rt, na.rm = T))  %>% 
  ggplot(aes(x = tr.num.bin, y = m_rt, fill = noise_condition)) +
  geom_boxplot(width = 0.2) +
  scale_y_continuous(limits=c(0,1.5)) + 
  labs(x = "Condition", y = "RT (sec)") +
  facet_wrap(~block, ncol = 1) +
  langcog::scale_fill_solarized()
```

## Statistical models

```{r}
d.model <- d.analysis %>% 
  filter(block == "block_2") %>% 
  mutate(correct = ifelse(shift_accuracy_clean == "correct", 1, 0))
```

Accuracy model

```{r}
m1.acc <- glmer(correct ~ noise_condition + (noise_condition|subid_short) + (1|target_image),
                data = d.model,
                family = "binomial")

summary(m1.acc)
```

RT model

```{r}
m1.rt  <- lmer(log(rt) ~ noise_condition * block + (noise_condition|subid_short) + (1|target_image), 
               data = d.model)

summary(m1.rt)
```
