---
title: "Speed-Acc Adult Noise-Gaze first shift"
author: "Kyle MacDonald"
output: html_document
---

## Set up 
 
```{r chunk_options, echo = F}
# code to clear workspace
rm(list=ls()) 

# set some global options
knitr::opts_chunk$set(warning=F, message=F, sanitize = T, 
                      fig.height=5, fig.width=8, echo=T, cache = F)
```

```{r}
# read in personal library of helper functions
source("../../helper_functions/libraries_and_functions.R")
```

## Load data

```{r}
d <- read_csv("../../../data/3_final_merged_data/first_shifts/speed_acc_adult_ng_fstshift_tidy.csv")
```

Remove participants who didn't pass data checks or who should be excluded for things like first language not English. 

```{r}
d %<>% filter(keep_runsheet == "yes", keep_et == "include")
```

## Check the data

```{r}
d %>% select(subid) %>% unique() %>% count()
```

Do we have 64 trials for each participant?

```{r}
d %>% 
  group_by(subid) %>% 
  select(tr.num) %>% 
  unique() %>% 
  count() %>% pull(n) == 64
```

Looks like we need to create a single variable that stores information about both the noise and gaze condition. 

```{r}
d %<>% mutate(condition_long = paste(gaze_condition, noise_condition, sep = "_"))
```

## Visualize data distributions

Reaction Times (RT)

```{r}
d %>% 
  filter(is.na(shift_accuracy) == F) %>% 
  ggplot(aes(x = rt, color = condition_long)) +
  geom_line(stat = "density", adjust = 1, size = 1) +
  facet_grid(response_onset_type~shift_accuracy) +
  theme(legend.position = "top") +
  theme_bw()
```

What about Accuracy? 

```{r}
d %>% 
  filter(response_onset_type == "noun", 
         shift_type %in% c("C_T", "C_D")) %>% 
  ggplot() +
  geom_bar(mapping = aes(x = as.factor(subid_short), fill = shift_accuracy)) +
  labs(x = "Participant ID") +
  facet_wrap(~condition_long, ncol = 1) +
  theme(legend.position = "top")
```

## Filter the data

Next, let's remove extreme RTs. 

```{r}
d.filt <- d %>% 
  filter(response_onset_type == "noun", 
         rt <= 5) %>% 
  mutate(shift_acc_num = ifelse(shift_accuracy == "correct", 1, 0))
```

### Visualize Accuracy

Let's visualize accuracy collapsing across the gaze and noise conditions. First we are going to summarise to get a proportion correct for each participant and condition. Then we aggregate again to get an overall proportion correct for each condition. 

```{r}
# aggregate accuracy at the participant level
ss.acc <- d.filt %>% 
  filter(!is.na(shift_accuracy)) %>% 
  group_by(condition_long, subid, shift_accuracy, gaze_condition, 
           noise_condition) %>% 
  summarise(n = n()) %>% 
  group_by(subid, condition_long, gaze_condition, noise_condition) %>% 
  mutate(total_trials = sum(n)) %>% 
  filter(total_trials >= 8) %>%
  mutate(prop = round(n / total_trials, 2)) 
```

Now make a boxplot of the accuracy data for each condition. Note that we have to first filter out the proprotion "incorrect" rows, so we are only seeing the proprotion correct data.

```{r}
acc_boxplot <- ss.acc %>% 
  filter(shift_accuracy == "correct") %>% 
  ggplot(aes(x = gaze_condition, y = prop)) +
  geom_boxplot(aes(fill = noise_condition), width = 0.2,
               notch = T, outlier.alpha = 0) +
  guides(fill = F) +
  scale_fill_manual(values = c("darkorange", "dodgerblue")) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  labs(x = "Gaze condition", y = "Prop. Correct") +
  ylim(0.3,1)

acc_boxplot
```

### Visualize Reaction Time

RT Boxplot

```{r}
ss.rt <- d.filt %>% 
  filter(!is.na(rt)) %>% 
  select(subid, condition_long, rt, gaze_condition, noise_condition) %>% 
  group_by(condition_long, subid, gaze_condition, noise_condition) %>% 
  mutate(n_trials = n()) %>% 
  filter(n_trials >= 8) %>% 
  summarise(m_rt = median(rt))
```

```{r}
rt_boxplot <- ss.rt %>% 
  ggplot(aes(x = fct_reorder(gaze_condition, m_rt, fun = "mean"), y = m_rt,
             fill = noise_condition)) +
  geom_boxplot(width = 0.2, notch = T, outlier.alpha = 0) +
  labs(x = "Gaze condition", y = "RT (sec)") +
  ylim(0.2, 1) +
  geom_quantile() +
  guides(fill=F) +
  scale_fill_manual(values = c("darkorange", "dodgerblue")) +
  theme(legend.position = "top") +
  labs(fill = "noise condition:")

rt_boxplot
```

```{r}
cowplot::plot_grid(rt_boxplot, acc_boxplot)
```

## RT Distributions

```{r}
acc_colors <- c("grey10", "black")
fill_vals <- c("grey90", "darkviolet")

p <- d %>% 
  filter(is.na(rt) == F, 
         response_onset_type == "noun") %>% 
  ggplot(aes(x = forcats::fct_reorder(noise_condition, rt, fun = "mean"), y = rt)) +
  ggbeeswarm::geom_quasirandom(shape = 21, color = "black", fill = "grey90") + 
  labs(y = "RT (sec)", x = NULL) +
  coord_flip() +
  facet_wrap(~gaze_condition, ncol = 1) +
  theme(legend.position = "top") 

p
```
