---
title: "Speed-acc kids data processing"
author: "Kyle MacDonald"
date: "October 1, 2015"
output: html_document
---

## Script to munge eye movement data

```{r libraries}
rm(list=ls())
source("R/helper_functions/libraries_v_3.6.R")
source("R/helper_functions/libraries_and_functions.R")
```

### Read in icharts for ASL kids/adults and Trio Series

We start with 5 iCharts.

* ASL data (both adults and kids)
* Trio Bull 26 months
* Trio Bull 36-39 months
* Trio Bull Adults
* Trio Face 26 months

Note the use of the colClasses function to set all variables to be read as characters.

```{r load data}
## ASL
sol_demo <- read.csv("data/demographics/sol_demo_all.csv", stringsAsFactors = F,
                     colClasses=c(rep("character", 
                                      length(scan("data/demographics/sol_demo_all.csv", 
                                                  sep=',', what="character" , nlines=1 )))))

sol_df <- read.csv("data/2_cleaned_data/sol-ichart-cleaned.csv", stringsAsFactors = F,
                   colClasses=c(rep("character",
                                    length(scan("data/2_cleaned_data/sol-ichart-cleaned.csv", 
                                                sep=',', what="character" , nlines=1 )))))

sol_n <- sol_df %>% 
    select(Sub.Num) %>% 
    unique() %>% 
    summarise(ASL = n())

## Trio Face
trio_face <- read.csv("data/2_cleaned_data/TrioFace26n24_cleaned.csv", stringsAsFactors = F, 
                      colClasses=c(rep("character",
                                    length(scan("data/2_cleaned_data/TrioFace26n24_cleaned.csv",
                                                sep=',', what="character" , nlines=1 )))))

trio_ps <- read.csv("data/trial_info/trio_prescreening_info.csv", sep = ",", 
                    stringsAsFactors = F,
                    colClasses=c(rep("character", 
                                     length(scan("data/trial_info/trio_prescreening_info.csv",
                                                 sep=',', what="character" , nlines=1 )))))

trio_n <- trio_face %>% 
    select(Sub.Num) %>% 
    unique() %>% 
    summarise(Face = n())

## Trio 26
trio_26 <- read.csv("data/2_cleaned_data/Trio_26_n18_cleaned.csv", stringsAsFactors = F,
                         colClasses=c(rep("character",
                                         length(scan("data/2_cleaned_data/Trio_26_n18_cleaned.csv",
                                                     sep=',', what="character" , nlines=1 )))))

trio_26_n <- trio_26 %>% 
    select(Sub.Num) %>% 
    unique() %>% 
    summarise(Trio_26 = n())

## Trio 36
trio_36 <- read.csv("data/2_cleaned_data/Trio36m_n22_cleaned.csv", 
                         stringsAsFactors = F,
                         colClasses=c(rep("character",
                                    length(scan("data/2_cleaned_data/Trio36m_n22_cleaned.csv",
                                                sep=',', what="character" , nlines=1 )))))

trio_36_n <- trio_36 %>% 
    select(Sub.Num) %>% 
    unique() %>% 
    summarise(Trio_36 = n())

## Trio Adults
trio_bull_adult <- read.csv("data/2_cleaned_data/TrioBullAdult_icharts_n7_cleaned.csv", 
                            stringsAsFactors = F,
                            colClasses=c(rep("character", length(scan("data/2_cleaned_data/TrioBullAdult_icharts_n7_cleaned.csv",
                                                                      sep=',', 
                                                         what="character" , nlines=1 )))))
trio_bull_adult_n <- trio_bull_adult %>% 
    select(Sub.Num) %>% 
    unique() %>% 
    summarise(Bull_Adult = n())

## Trio Bull
trio_bull_26 <- read.csv("data/2_cleaned_data/TrioBullAA26n18_cleaned.csv",
                         stringsAsFactors = F,
                         colClasses=c(rep("character",
                                          length(scan("data/2_cleaned_data/TrioBullAA26n18_cleaned.csv",
                                                      sep=',', what="character" , nlines=1 )))))

trio_bull_26_n <- trio_bull_26 %>% 
    select(Sub.Num) %>% 
    unique() %>% 
    summarise(Bull_26 = n())
```

```{r}
df_n <- data.frame(ASL = sol_n$ASL, Face = trio_n$Face, 
                   Trio_26 = trio_26_n$Trio_26, 
                   Trio_36 = trio_36_n$Trio_36, 
                   Bull_Adult = trio_bull_adult_n$Bull_Adult, 
                   Bull_26 = trio_bull_26_n$Bull_26) %>% 
    mutate(Total_n = ASL + Face + Trio_26 + Trio_36 + Bull_Adult + Bull_26)
           
knitr::kable(df_n)
```

Add Trio Face prescreening info to iChart.

```{r}
trio_ps %<>%
    select(Sub.Num, PSO.Reason, Tr.Num) %>% 
    mutate(Sub.Num = as.character(Sub.Num),
           Tr.Num = as.character(Tr.Num))

trio_face <- left_join(x = trio_face, y = trio_ps, by = c("Sub.Num", "Tr.Num"))
```

### Add variables to track language, center stimuli, and age bin within kids

```{r}
sol_df %<>% mutate(language_modality = "ASL", experiment = "ASl") 

## add adults ages to demo sheet
sol_demo <- sol_df %>% 
    filter(as.numeric(Months) > 100) %>% 
    select(Sub.Num, Months) %>% 
    unique() %>% 
    left_join(sol_demo, ., by = "Sub.Num")

sol_demo %<>% mutate(Months = ifelse(is.na(Months), age_peek_months, Months))

include <- sol_demo %>%
    select(Sub.Num, include,
           reason_excluded, stimuli,
           age_code, signs_produced, 
           hearing_status_participant,
           Months) 

sol_df  <- left_join(sol_df, include, by = c("Sub.Num", "stimuli", "Months")) %>% 
    mutate(age_code = ifelse(as.numeric(Months) > 60, "adult", "child"))

sol_df %<>% filter(include == "yes")
```


```{r}
trio_face %<>% mutate(language_modality = "English", stimuli = "Face", 
                      experiment = "Trio_Face", age_code = "child", 
                      hearing_status_participant = "hearing")

trio_26 %<>% mutate(language_modality = "English", stimuli = "Trio", 
                    experiment = "Trio_26", age_code = "child", 
                    hearing_status_participant = "hearing")

trio_36 %<>% mutate(language_modality = "English", stimuli = "Trio", 
                    experiment = "Trio_36",  age_code = "child",
                    hearing_status_participant = "hearing")

trio_bull_adult %<>% mutate(language_modality = "English", stimuli = "Bull", 
                            experiment = "Trio_Bull", age_code = "adult",
                            hearing_status_participant = "hearing")

trio_bull_26 %<>% mutate(language_modality = "English", stimuli = "Bull", 
                         experiment = "Trio_Bull",  age_code = "child",
                         hearing_status_participant = "hearing")
```

### Filter all data to keep frames 0 - 3000

3000ms is the shortest window out of all 5 datasets (trio_face). So we have to match this window.

```{r}
sol_df_final <- sol_df %>% 
    select(Sub.Num, Months, Tr.Num, stimuli, Months, experiment, age_code,
           hearing_status_participant, Prescreen.Notes, language_modality, X0:X3000) 

trio_face_final <- trio_face %>% 
    select(Sub.Num, Months, Tr.Num, stimuli, Months, experiment, age_code,
           hearing_status_participant, Prescreen.Notes, language_modality, X0:X3000) 

trio_26_final <- trio_26 %>%
    select(Sub.Num, Months, Tr.Num, stimuli, Months, experiment, age_code,
           hearing_status_participant, Prescreen.Notes, language_modality, X0:X3000) 

trio_36_final <- trio_36 %>%
    select(Sub.Num, Months, Tr.Num, stimuli, Months, experiment, age_code,
           hearing_status_participant, Prescreen.Notes, language_modality, X0:X3000) 

trio_bull_adult_final <- trio_bull_adult %>%
    select(Sub.Num, Months, Tr.Num, stimuli, Months, experiment, age_code,
           hearing_status_participant, Prescreen.Notes, language_modality, X0:X3000) 

trio_bull_26_final <- trio_bull_26 %>% 
    select(Sub.Num, Months, Tr.Num, stimuli, Months, experiment, age_code,
           hearing_status_participant, Prescreen.Notes, language_modality, X0:X3000) 
```

### Bind data frames together

```{r}
speed_acc_df_final <- bind_rows(sol_df_final, trio_face_final, trio_26_final, trio_36_final, trio_bull_adult_final, trio_bull_26_final)
```

## Munge and process eye movement data

Our goal is to get a tidy data table with an RT and correct/incorrect for each good trial.

```{r}
iChart <- speed_acc_df_final 
```

## Replace 2s with 0.5s

Recode all 2s as 0.5s (center-looking). Prior versions of datawiz coded center looking as 2s. 

```{r}
iChart_recode <- as.data.frame(apply(select(iChart, X0:X3000), 2,
                                     function(x) ifelse(x == "2", "0.5", x)),
                        stringsAsFactors = F)

iChart <- iChart %>% 
    select(Sub.Num:language_modality) %>% 
    bind_cols(iChart_recode)
```

## Filter dataset

Filter out participants that should not go into analyses based on exclusionary criteria: a) age, b) didn’t know signs in the task, c) not enough ASL exposure.

```{r}
# check how many ss we have before starting to filter
iChart %>% 
    select(Sub.Num, age_code, experiment, language_modality) %>% 
    group_by(language_modality, age_code, experiment) %>% 
    unique() %>% 
    summarise(count = n())
```

### Get number of ss

For each age and language (English, ASL)

```{r}
iChart %>% 
    select(Sub.Num, age_code, language_modality) %>% 
    group_by(language_modality, age_code) %>% 
    unique() %>% 
    summarise(count = n())
```

### Remove ss for too few trials

```{r}
ss_prescreened <- iChart %>% 
    filter(Prescreen.Notes != "") %>% 
    group_by(Sub.Num) %>% 
    select(Sub.Num, Prescreen.Notes) %>% 
    summarise(num_prescreened = n())

total_trials <- 32
trials_cut_point <- total_trials * .25

ss_trials_df <- iChart %>% 
    group_by(Sub.Num) %>% 
    summarise(Trials = n()) 

ss_trials_df <- left_join(ss_trials_df, ss_prescreened) %>% 
    mutate(num_prescreened = ifelse(is.na(num_prescreened), 0, num_prescreened),
        n_good_trials = Trials - num_prescreened)

trials_filter <- ss_trials_df %>% 
    mutate(exclude_few_trials = ifelse(n_good_trials <= trials_cut_point, 
                                       "exclude", "include")) %>% 
    select(Sub.Num, exclude_few_trials)

# get the number of participants removed by filter
trials_filter %>% group_by(exclude_few_trials) %>% dplyr::summarise(n())

# merge filtering information with iChart
iChart <- left_join(iChart, trials_filter, by = "Sub.Num")

# now filter
iChart <- filter(iChart, exclude_few_trials == "include")
```

```{r}
iChart %>% 
    select(Sub.Num, age_code, language_modality) %>% 
    group_by(language_modality, age_code) %>% 
    unique() %>% 
    summarise(n())
```

### Remove prescreened out trials

```{r}
iChart <- filter(iChart, Prescreen.Notes == "" | is.na(Prescreen.Notes))
```

### Process iChart

First, we need to process the data, keeping only those trials on which the child was looking at the signer at F0.

* C: Center
* D: Distractor
* T: Target
* A: Away

includeOffCenter == FALSE -> only include trials child was looking at center at F0

includeOffCenter == TRUE -> include trials child was looking at center, target, or distractor at F0

```{r}
colnames(iChart) <- sapply(colnames(iChart), function (x) {
    str_replace(x, "X", "")  
})
```

```{r}
iChart %>% group_by(`0`) %>% summarise(n())

# Where were ss looking at F0?
iChart <- iChart %>% 
    mutate(Response = ifelse(`0` == "0.5" | `0` == ".5", "D", 
                             ifelse(`0` == "0", "A",
                                    ifelse(`0` == "1", "A", "A"))))

iChart %>% group_by("0", Response) %>% dplyr::summarise(Trials = n())

# change all trials to "Vanilla" 
iChart$Condition <- "Vanilla"
```

### Flag C-T and C-D Trials

Datawiz does not tell us which shifts land on a target vs. a disctractor. So we need to use a function that flags each trial as one of the following:

* C_T: center to target
* C_D: center to distractor
* C-C: center to center (child leaves the signer, goes away, and comes back to signer)
* no_shift
* off_center

```{r}
# apply fun to each row in our dataset to flag trial type
trial_types <- apply(iChart, 1, score_trial_type_lwl, start = "0", end = "3000") %>% 
    t() %>% 
    as.data.frame(stringsAsFactors=F) %>% 
    rename(trial_type = V1, RT = V2)
    

# merge trial type information with iChart
iChart <- cbind(iChart, trial_types)
```

```{r}
iChart %>% group_by(trial_type) %>% dplyr::summarise(Trials = n())
```

### Create summary table

First we need to get C_T proportions for each participant 

```{r}
iChart$Response <- as.vector(iChart$Response)

ss <- iChart %>%
    filter(trial_type %in% c("C_T", "C_D", "C_C", "no_shift")) %>% 
    select(Sub.Num:language_modality, trial_type, age_code, RT) %>% 
    mutate(age_years = as.numeric(Months) / 12,
           RT_sec = as.numeric(RT) / 1000,
           correct = ifelse(trial_type == "C_T", 1, 0))
```

Get final n for each age group and language

```{r}
iChart %>% 
    select(Sub.Num, age_code, language_modality) %>% 
    group_by(language_modality, age_code) %>% 
    unique() %>% 
    count()
```

### Save final/processed tidy data frame

```{r}
write.csv(iChart, file = "3_final_merged_data/speed-acc-cleaned-iChart.csv", 
          row.names = F, na = "NA")

write.csv(ss, file = "3_final_merged_data/speed-acc-ss-df.csv", 
          row.names = F, na = "NA")
```