---
title: "Speed-Acc Statistical Models"
output: html_document
---

## Setup

This document contains the codebase for the bayesian data analysis of Experiment 3 ('noise') in the paper, "An information-seeking account of children's eye movements during grounded signed and spoken language comprehension."

```{r set global_options, include=FALSE}
library(here)
source(here::here("R/helper_functions/libraries_and_functions.R"))
source(here::here("R/helper_functions/ewma_helper_funs.R"))

data_path <- "data/3_final_merged_data/first_shifts/"
ewma_path <- "data/3_final_merged_data/ewma_output/"
hddm_path <- "data/3_final_merged_data/hddm_output/"
write_path <- "data/3_final_merged_data/bda_posterior_samples/"

options(mc.cores=parallel::detectCores())
set.seed (3875)
```

Read adult and child data.

```{r read data}
d_kids_noise <- read_csv(here::here(data_path, "speed_acc_child_noise_fstshift_tidy.csv")) 
d_adults <- read_csv(here::here(data_path, "speed_acc_adult_ng_fstshift_tidy.csv")) 
```

Merge datasets.

```{r clean datasets and merge}
d_adults %<>% select(-age)

d_kids_noise %<>% mutate(gaze_condition = ifelse(gaze_condition == "no_gaze", 
                                                 "straight_ahead", 
                                                 gaze_condition))

d <- bind_rows(mutate(d_kids_noise, experiment = "kids_noise", age_category = "children"),
               mutate(d_adults, experiment = "adults_ng", age_category = "adults")) %>% 
  select(-resp_onset_type_fact, -subid_short) %>% 
  mutate(age_category = factor(age_category) %>% fct_rev()) 

# test that we have the right number of rows after the merge (result should be TRUE)
nrow(d_kids_noise) + nrow(d_adults) == nrow(d)
```

## Accuracy models

```{r filter e1 data}
d_e1_analysis <- d %>% 
  filter(keep_runsheet %in% c("yes", "keep"), 
         keep_et == "include",
         gaze_condition == "straight_ahead",
         !is.na(rt)) %>% 
  filter(rt <= mean(rt) + 3*sd(rt),
         rt >= mean(rt) - 3*sd(rt),
         rt <= 1.5,
         response_onset_type == "noun", 
         shift_start_location == "center") %>% 
  mutate(shift_acc_num = ifelse(shift_accuracy_clean == "correct", 1, 0),
         log_rt = log(rt))
```

### Accuracy age (categorical)

```{r fit acc noise model}
m_bglm_acc_e1 <- stan_glmer(
  shift_acc_num ~ noise_condition + age_category + (noise_condition | subid) + (noise_condition | target_image), 
  data = d_e1_analysis,
  family = binomial(link = "logit"), 
  prior = normal(0, 2),
  prior_intercept = normal(0, 1),
  prior_covariance = decov(regularization = 2), 
  adapt_delta = 0.99,
  chains = 4)

# ACC age-categorical
samples_e1_acc <- m_bglm_acc_e1 %>% 
  as.data.frame() %>% as_tibble() %>% 
  dplyr::rename(clear_children = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age_categoryadults) %>% 
  select(clear_children, noise_beta, age_beta)
```

### Accuracy age (categorical) interaction

```{r fit acc noise model interaction}
m_bglm_acc_e1_int <- stan_glmer(
  shift_acc_num ~ noise_condition * age_category + (noise_condition | subid) + (noise_condition | target_image), 
  data = d_e1_analysis,
  family = binomial(link = "logit"), 
  prior = normal(0, 2),
  prior_intercept = normal(0, 1),
  adapt_delta = 0.99,
  prior_covariance = decov(regularization = 2), # prior on Covariance matrices for mixed effects model
  chains = 4)

samples_e1_acc_int <- m_bglm_acc_e1_int %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_children = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age_categoryadults,
                int_beta = `noise_conditionnoise:age_categoryadults`) %>% 
  select(clear_children, noise_beta, age_beta, int_beta)
```

### Accuracy Age (continuous)

```{r fit acc noise model continous age}
m_bglm_acc_contAge_e1 <- stan_glmer(
  shift_acc_num ~ noise_condition + age + (noise_condition | subid) + (noise_condition | target_image), 
  data = filter(d_e1_analysis, age_category == "children"),
  family = binomial(link = "logit"), 
  prior = normal(0, 2),
  adapt_delta = 0.99,
  prior_intercept = normal(0, 1),
  prior_covariance = decov(regularization = 2), # prior on Covariance matrices for mixed effects model
  chains = 4)

# ACC age-continous
samples_e1_acc_age_cont <- m_bglm_acc_contAge_e1 %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_children = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age) %>% 
  select(clear_children, noise_beta, age_beta)
```

### Accuracy Age (continuous) Interaction

```{r fit acc noise age continuous interaction}
m_bglm_acc_int_e1 <- stan_glmer(
  shift_acc_num ~ noise_condition * age + (noise_condition | subid) + (noise_condition | target_image), 
  data = filter(d_e1_analysis, age_category == "children"),
  family = binomial(link = "logit"), 
  prior = normal(0, 2),
  prior_intercept = normal(0, 1),
  prior_covariance = decov(regularization = 2), # prior on Covariance matrices for mixed effects model
  chains = 4)

# ACC age-interaction
samples_e1_acc_age_int <- m_bglm_acc_int_e1 %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_children = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age,
                int_beta = `noise_conditionnoise:age`) %>% 
  select(clear_children, noise_beta, age_beta, int_beta)
```

## RT models

### RT age (categorical)

```{r fit rt noise model age categorical}
m_bglm_rt_e1 <- stan_glmer(
  log_rt ~ noise_condition + age_category + (noise_condition | subid) + (noise_condition | target_image), 
  family = gaussian(),
  data = d_e1_analysis,
  prior = normal(0, 2), 
  prior_intercept = normal(0, 5),
  prior_covariance = decov(regularization = 2), # prior on Covariance matrices for mixed effects model
  chains = 4)

## RT age-categorical
samples_e1_rt <- m_bglm_rt_e1 %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_children = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age_categoryadults) %>% 
  select(clear_children, noise_beta, age_beta)
```

### RT age (categorical) interaction

```{r fit rt noise model interaction}
m_bglm_rt_e1_int <- stan_glmer(
  log_rt ~ noise_condition * age_category + (noise_condition | subid) + (noise_condition | target_image), 
  family = gaussian(),
  data = d_e1_analysis,
  prior = normal(0, 2), 
  prior_intercept = normal(0, 5),
  prior_covariance = decov(regularization = 2), # prior on Covariance matrices for mixed effects model
  chains = 4)

## RT age-continous interaction
samples_e1_rt_age_cont_int <- m_bglm_rt_e1_int %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_children = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age_categoryadults,
                int_beta = `noise_conditionnoise:age_categoryadults`) %>% 
  select(clear_children, noise_beta, age_beta, int_beta)
```

### RT age (continous)

```{r fit rt noise age continous}
m_bglm_rt_contAge_e1 <- stan_glmer(
  log_rt ~ noise_condition + age + (noise_condition | subid) + (noise_condition | target_image), 
  family = gaussian(),
  data = filter(d_e1_analysis, age_category == "children"),
  prior = normal(0, 2), 
  prior_intercept = normal(0, 5),
  prior_covariance = decov(regularization = 2), # prior on Covariance matrices for mixed effects model
  chains = 4)

## RT age-continuous
samples_e1_rt_age_cont <- m_bglm_rt_contAge_e1 %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_children = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age) %>% 
  select(clear_children, noise_beta, age_beta)
```

### RT age (continuous) Interaction

```{r fit rt age interaction noise}
m_bglm_rt_contAge_int_e1 <- stan_glmer(
  log_rt ~ noise_condition * age + (noise_condition | subid) + (noise_condition | target_image), 
  family = gaussian(),
  data = filter(d_e1_analysis, age_category == "children"),
  prior = normal(0, 2), 
  prior_intercept = normal(0, 5),
  prior_covariance = decov(regularization = 2), # prior on Covariance matrices for mixed effects model
  chains = 4)

## RT age-interaction
samples_e1_rt_age_int <- m_bglm_rt_contAge_int_e1 %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_children = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age,
                int_beta = `noise_conditionnoise:age`) %>% 
  select(clear_children, noise_beta, age_beta, int_beta)
```

Tidy up the posterior samples.

```{r tidy up the samples noise}
# tidy up accuracy
samples_e1_acc_tidy <- samples_e1_acc %>% 
  mutate(noise_children = clear_children + noise_beta,
         clear_adults = clear_children + age_beta, 
         noise_adults = clear_children + noise_beta + age_beta,
         sample_id = 1:n()) %>% 
  gather(key = condition, value = param_est, -sample_id, -noise_beta, -age_beta) %>% 
  mutate(acc_prob_scale = logit_to_prob(param_est)) %>% 
  separate(condition, into = c("noise_condition", "age_category"))

# tidy up rt samples
samples_e1_rt_tidy <- samples_e1_rt %>% 
  mutate(noise_children = clear_children + noise_beta,
         clear_adults = clear_children + age_beta, 
         noise_adults = clear_children + noise_beta + age_beta,
         sample_id = 1:n()) %>% 
  gather(key = condition, value = param_est, -sample_id, -noise_beta, -age_beta) %>% 
  mutate(rt_ms_scale = exp(param_est)) %>% 
  separate(condition, into = c("noise_condition", "age_category")) 
```


## EWMA models

Read in EWMA output. 

```{r read ewma output noise}
noise_ewma_files <- c("speed_acc_kids_noise_ewma_results.csv", "speed_acc_adult_ng_ewma_results.csv")

d_ewma_noise <- noise_ewma_files %>% 
  purrr::map_df(read_ewma, path = ewma_path) 
```

### Noise experiment

Filter to select just the noise and clear conditions.

```{r filter ewma results noise}
d_ewma_noise %<>% 
  filter(experiment %in% c("noise", "noise_gaze"),
         condition %in% c("clear", 
                          "noise", 
                          "straight_ahead_noise", 
                          "straight_ahead_clear")) %>% 
  mutate(noise_condition = ifelse(str_detect(condition, "noise"), "noise", "clear"),
         age_category = ifelse(age_code == "child", "children", "adults")) 

# create data frame with age for kids as continous predictor
d_age_cont_ewma <- d_kids_noise %>% 
  select(subid_short, age) %>%
  rename(subid = subid_short) %>% 
  unique() %>% 
  mutate(subid = as.character(subid)) %>% 
  left_join(select(d_ewma_noise, -age), ., by = "subid") %>% 
  filter(age_category == "children")
```

#### EWMA cut point (noise) 

```{r fit cutpoints model ewma noise, eval = F}
ss_cutoffs_noise <- d_ewma_noise %>% 
  filter(guess == "response") %>% 
  group_by(subid, noise_condition, age_category) %>% 
  summarise_(cutoff = interp(~ min(x), x = as.name("rt"))) %>% 
  mutate(log_cut = log(cutoff))

# fit model
m_cutoffs <- stan_lm(cutoff ~ noise_condition + age_category, 
                     data = ss_cutoffs_noise,
                     prior = R2(0.75, what = "mean"))

# get posterior samples
samples_ewma_cuts_noise <- m_cutoffs %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_adults = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age_categorychildren) %>% 
  select(clear_adults, noise_beta, age_beta) %>% 
  mutate(clear_children = clear_adults + age_beta,
         noise_children = clear_adults + age_beta + noise_beta, 
         noise_adults = clear_adults + noise_beta,
         sample_id = 1:n()) %>% 
  gather(key = condition, value = param_est, -sample_id, -noise_beta, -age_beta) %>% 
  separate(condition, into = c("noise_condition", "age_category"))
```

#### EWMA guessing (noise)

```{r fit aggregate prop guessing ewma nosie}
# fit model
m_guessing_noise <- stan_glmer(
  guess_num ~ noise_condition + age_category + (noise_condition | subid),
  data = d_ewma_noise,
  prior = normal(0, 2),
  prior_intercept = normal(0, 1),
  prior_covariance = decov(regularization = 2), 
  chains = 4)

# get posterior samples
samples_ewma_guess_noise <- m_guessing_noise %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_adults = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age_categorychildren) %>% 
  select(clear_adults, noise_beta, age_beta) %>% 
  mutate(clear_children = clear_adults + age_beta,
         noise_children = clear_adults + age_beta + noise_beta, 
         noise_adults = clear_adults + noise_beta,
         sample_id = 1:n()) %>% 
  gather(key = condition, value = param_est, -sample_id, -noise_beta, -age_beta) %>% 
  separate(condition, into = c("noise_condition", "age_category"))
```

Fit a model with age as continous predictor just within the child sample.

```{r fit prop guessing ewma age continous noise}
# fit model
m_guessing_noise_ageCont <- stan_glmer(
  guess_num ~ noise_condition + age + (noise_condition | subid),
  data = d_age_cont_ewma,
  prior = normal(0, 2),
  prior_intercept = normal(0, 1),
  prior_covariance = decov(regularization = 2), 
  chains = 4)

# get posterior samples
samples_ewma_guess_noise_ageCont <- m_guessing_noise_ageCont %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_children = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age) %>% 
  select(clear_children, noise_beta, age_beta)
```

Fit the same model with an interaction term

```{r fit ewma guessing age interaction model noise, eval = F}
# fit model
m_guessing_noise_ageInt <- stan_glmer(
  guess_num ~ noise_condition * age + (noise_condition | subid),
  data = d_age_cont_ewma,
  prior = normal(0, 2),
  prior_intercept = normal(0, 1),
  prior_covariance = decov(regularization = 2), 
  chains = 4
)

# get posterior samples
samples_ewma_guess_noise_ageInt <- m_guessing_noise_ageInt %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  dplyr::rename(clear_children = `(Intercept)`,
                noise_beta = noise_conditionnoise,
                age_beta = age,
                int_beta = `noise_conditionnoise:age`) %>% 
  select(clear_children, noise_beta, age_beta, int_beta)
```

## Save the posterior samples 

```{r save samples from all models}
posteriors <- list(rt_noise = samples_e1_rt_tidy,
                   rt_noise_age = samples_e1_rt_age_cont,
                   acc_noise = samples_e1_acc_tidy,
                   acc_noise_age = samples_e1_acc_age_cont,
                   ewma_guess_noise = samples_ewma_guess_noise,
                   ewma_guess_noise_age = samples_ewma_guess_noise_ageCont)

saveRDS(posteriors, file = here::here(write_path, "speed-acc-noise-posterior-samples.rds"))

beepr::beep(sound = 3)
```