---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

This script plots and analyzes the timecrouse eye-tracking data for an experiment comparing speed-accuracy tradeoffs when establishing reference in real-time. We vary the information value and saliency of the center fixation and measure the effects on accuracy and RT.

## Setup

Load libraries and read in tidy data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F, warning=F, cache=F, message=F, sanitize = T, results = 'asis')
source("../../helper_functions/libraries_and_functions.R")
```

Read data. 

```{r read data}
d <- read_csv("../../../data/3_final_merged_data/timecourse/speed_acc_adult_ng_timecourse_tidy.csv.gz")
```

Create condition column

```{r}
d %<>% mutate(condition = paste(gaze_condition, noise_condition, sep = "_"))
```

## Visualize looking behavior 

Filter to get the analysis window (one second before the noun onset). Start is when the center fixation appeared. End is the end of the trial. 

```{r}
d.filt <- d %>% filter(t.stim > 0, t.stim <= 9) 
```

First, we generate curves that represent center, target, and distractor looking over time

Summarize data for each ROI for each participant and each time slice.

```{r}
# get number of trials looking at each gaze target for each time slice
ss.d <- d.filt %>% 
  group_by(subid, t.stim, condition) %>% 
  summarise(count = n()) %>% 
  ungroup() %>% 
  complete(nesting(subid, t.stim), condition,
           fill = list(count = 0)) %>% 
  mutate(subid = as.character(subid))

# get proportion looking by dividing the freq looking at each target by the total looking 
# derived in step 1 of this chunk
ss.d <- as.data.frame(xtabs(~ subid + t.stim + target_looking + condition, 
                            data = d.filt),
                      stringsAsFactors = F) %>% 
  mutate(t.stim = as.numeric(t.stim)) %>% 
  left_join(x = ss.d, y = ., by = c("subid", "t.stim", "condition")) %>% 
  mutate(proportion_looking = Freq / count)
```

Get means and CIs for proportion looking at each time slice across particpants

```{r}
ms.means.timeslice <- ss.d %>% 
  group_by(t.stim, condition, target_looking) %>% 
  summarise(mean = mean(proportion_looking, na.rm = T)) %>% 
  mutate(gaze_condition = ifelse(str_detect(condition, "no_gaze"), "no_gaze", "gaze"),
         noise_condition = ifelse(str_detect(condition, "no_noise"), "no_noise", "noise"))
```

Now make the Tanenhaus style curves for each condition 

```{r}
ms.means.timeslice %>% 
  #filter(target_looking == "center") %>% 
  ggplot(aes(x = as.numeric(t.stim), y = mean, 
           color = target_looking, linetype = noise_condition), data = .) + 
  ylim(0,1) +
  xlim(-0.5,10) +
  geom_line(size=1) +
  facet_wrap(~gaze_condition, ncol = 1) +
  xlab("Time in sec from onset of trial") +
  geom_vline(xintercept = mean(d$noun_onset_seconds), linetype = "dashed") +
  geom_vline(xintercept = mean(d$sentence_onset_seconds), linetype = "dashed") +
  ylab("Proportion looking") +
  #geom_dl(aes(label = condition), method = "first.bumpup") +
  annotate("text", label = "Sentence Onset", x = mean(d$sentence_onset_seconds)-0.3, 
           y = 0.4, size = 4, colour = "dodgerblue") +
  annotate("text", label = "Noun Onset", x = mean(d$noun_onset_seconds)-0.3, 
           y = 0.4, size = 4 , colour = "dodgerblue") +
  theme(text = element_text(size = 16)) +
  theme_bw()
```

We can do the same thing to compare the effect of gaze across the noise conditions.

```{r}
ms.means.timeslice %>% 
  #filter(target_looking == "center") %>% 
  ggplot(aes(x = as.numeric(t.stim), y = mean, 
           color = target_looking, linetype = gaze_condition), data = .) + 
  ylim(0,1) +
  xlim(-0.5,10) +
  geom_line(size=1) +
  facet_wrap(~noise_condition, ncol = 1) +
  xlab("Time in sec from onset of trial") +
  geom_vline(xintercept = mean(d$noun_onset_seconds), linetype = "dashed") +
  geom_vline(xintercept = mean(d$sentence_onset_seconds), linetype = "dashed") +
  ylab("Proportion looking") +
  #geom_dl(aes(label = condition), method = "first.bumpup") +
  annotate("text", label = "Sentence Onset", x = mean(d$sentence_onset_seconds)-0.3, 
           y = 0.4, size = 4, colour = "dodgerblue") +
  annotate("text", label = "Noun Onset", x = mean(d$noun_onset_seconds)-0.3, 
           y = 0.4, size = 4 , colour = "dodgerblue") +
  theme(text = element_text(size = 16)) +
  theme_bw()
```


## Standard "window" accuracy analyses

### Boxplot of proportion looking to each ROI as a function of condition.

First we need to filter to get the analysis window

```{r}
d.analysis <- d.filt %>% filter(t.rel.noun >= 0)  
```

Then we get the proportion looking to each location for each trial for each participant.

```{r}
# get number of trials looking at each gaze target for each time slice
ss.d.tr <- d.analysis %>% 
  group_by(subid, tr.num, condition) %>% 
  summarise(count = n()) %>% 
  ungroup() %>% 
  mutate(subid = as.character(subid))

# get proportion looking by dividing the freq looking at each target by the total looking 
# derived in step 1 of this chunk
ss.d.tr <- as.data.frame(xtabs(~ subid + tr.num + target_looking + condition,
                            data = d.analysis),
                      stringsAsFactors = F) %>% 
  mutate(tr.num = as.numeric(tr.num)) %>% 
  left_join(x = ss.d.tr, y = ., by = c("subid", "tr.num", "condition")) %>%
  mutate(proportion_looking = Freq / count) %>% 
  group_by(subid, condition, target_looking) %>% 
  summarise(m_prop_looking = mean(proportion_looking, na.rm = T))
```

Now we can plot the trial level summarized looking data. Here we use a boxplot to show both raw and summaries of the data. 

```{r, fig.width=8}
ggplot(aes(x= target_looking, y = m_prop_looking, fill = condition), 
       data = ss.d.tr) +
  geom_boxplot(alpha = 0.8) +
  geom_point(alpha = 0.6, 
             position = position_jitterdodge(jitter.width = 0.1,
                                             dodge.width = 0.75)) +
  labs(x = "Gaze Location",
       y = "Prop. Looking") +
  theme(text = element_text(size = 16))
```

KM: STOPPED HERE

### Analyze looking behavior prior to central fixation onset 

```{r}
d.order.analysis <- d.filt %>% 
  filter(t.rel.center.fixation <= 0) %>%
  group_by(subid, tr.num, condition, target_looking) %>%
  summarise(count = n()) %>% 
  ungroup() %>% 
  complete(nesting(subid, tr.num, condition), target_looking, 
           fill = list(count=0)) %>% 
  group_by(subid, tr.num) %>%
  mutate(prop_looking = count / sum(count))
```

```{r}
d.order.analysis %>% 
  ggplot(aes(x = prop_looking, fill = condition)) + 
  geom_density(alpha = 0.5) +
  facet_wrap(~target_looking) + 
  theme_bw()
```

### Does looking to center prior to fixation onset change over time in the task?

```{r}
d.order.analysis %>% 
  ungroup() %>% 
  filter(target_looking == "center") %>% 
  mutate(tr.num = as.numeric(tr.num), 
         tr.binned = cut(tr.num, breaks = 6)) %>% 
  group_by(tr.binned) %>% 
  summarise(m = mean(prop_looking),
            ci = (qnorm(0.975)*sd(prop_looking)) / sqrt(length(prop_looking))) %>% 
  ggplot(aes(x = tr.binned, y = m)) + 
  geom_pointrange(aes(ymin = m - ci, ymax = m + ci)) +
  geom_line(group = 1, size = 1) +
  ylim(0.4, 1) +
  geom_hline(yintercept = 0.5, linetype = "dashed")  +
  labs(x = "Binned Trial Number", 
       y = "Prop. Looks to Center",
       title = "Anticipatory looking to center") +
  theme(text = element_text(size = 16))
```

Looks like there is a an increase in looking away from the two target images to the center area as the task unfolds. I think this is an anticipation effect -- Participants know that the information source is going to appear in the same spot, so they fixate there.

But this analysis ignores the different conditions. This is what we look at next:

```{r}
create_tr_num_fun <- function(data_frame) {
  
  rows_df <- data_frame %>% 
    select(subid, condition, tr.num) %>% 
    unique() %>% 
    nrow()
  
  data_frame %<>% 
    select(subid, condition, tr.num) %>% 
    unique() %>% 
    mutate(tr_cond = seq(1, rows_df),
           block = ifelse(tr.num <= 24, 1, 
                          ifelse(tr.num > 24 & tr.num <= 48, 2, 
                                 ifelse(tr.num > 48 & tr.num <= 72, 3, 4)))) %>% 
    left_join(data_frame, ., by = c("subid", "tr.num", "condition"))
  
  data_frame
}
```

Add the trial number within condition to our data frame.

```{r}
d.order.analysis %<>% 
  group_by(condition, subid) %>% 
  do(create_tr_num_fun(data_frame = .))
```

Now summarise and plot.

```{r}
d.order.analysis %>% 
  ungroup() %>% 
  filter(target_looking == "center") %>% 
    mutate(tr_cond = as.numeric(tr_cond), 
         tr.binned = cut(tr_cond, breaks = 4)) %>% 
  group_by(tr.binned, condition) %>% 
  summarise(m = mean(prop_looking),
            ci = (qnorm(0.975)*sd(prop_looking)) / sqrt(length(prop_looking))) %>% 
  ggplot(aes(x = tr.binned, y = m, color = condition, group = condition)) + 
  geom_pointrange(aes(ymin = m - ci, ymax = m + ci), 
                  position = position_jitter(width = 0.05)) +
  geom_line(size = 1) +
  ylim(0.4, 1) +
  scale_x_discrete(expand = c(-0.5,1.2)) +
  guides(color=F) +
  geom_dl(aes(label = condition), method = list("first.bumpup", hjust = 1.1, cex = 1.2)) +
  geom_hline(yintercept = 0.5, linetype = "dashed")  +
  labs(x = "Binned Trial Number", 
       y = "Prop. Looks to Center",
       title = "Change in anticipatory looking to center") 
```
