---
title: "SOL Speed-Accuracy"
author: "Kyle MacDonald"
date: "October 1, 2015"
output: html_document
---

# Data processing, plotting, and analysis script 

```{r chunk_options}
rm(list=ls())
knitr::opts_chunk$set(warning=FALSE, message=FALSE, sanitize = T, 
                      fig.height=8, fig.width=10, echo=F, cache = T)
```

```{r, echo=FALSE, warning=F, message=F}
source("../helpers/libraries_v_3.6.R")
source("../helpers/useful.R")
library(magrittr)
library(stringr)
library(GGally)
library(kmr)
library(dplyr)
library(tidyr)
```

## Read Data

Demographics

```{r}
sol_demo <- read.csv("../../raw_data/sol_demo_all.csv", stringsAsFactors = F)
sol_demo$Sub.Num <- as.character(sol_demo$Sub.Num)
```

Eye movement data

```{r}
iChart <- read.csv("../../processed_data/speed-accuracy/sol-speed-acc-final-iChart.csv", 
                   check.names=F, stringsAsFactors=F)

iChart %<>% mutate(Sub.Num =  as.character(Sub.Num))
```

## Filter dataset

Filter out participants that should not go into analyses based on exclusionary criteria: a) age, b) didn’t know signs in the task, c) not enough ASL exposure.

```{r}
exclude <- sol_demo %>% 
    filter(include == "no", age_code != "adult") %>% 
    select(Sub.Num, reason_excluded) 

include <- sol_demo %>%
    select(Sub.Num, include,
           reason_excluded, stimuli,
           age_code, signs_produced, 
           hearing_status_participant)

iChart <- left_join(iChart, include, by = c("Sub.Num", "stimuli")) 

iChart <- iChart %>% 
    filter(include == "yes" | language_modality == "English") %>% 
    mutate(age_code = ifelse(language_modality == "English", "child", age_code),
           hearing_status_participant = ifelse(language_modality == "English", 
                                               "hearing", hearing_status_participant))
```

### Remove prescreened out trials

```{r}
ss_prescreened <- iChart %>% 
    group_by(Sub.Num) %>% 
    filter(Prescreen.Notes != "") %>% 
    dplyr::summarise(num_prescreened = n())

iChart <- filter(iChart, Prescreen.Notes == "")
```

### Process iChart

First, we need to process the data, keeping only those trials on which the child was looking at the signer at F0.

* C: Center
* D: Distractor
* T: Target
* A: Away

includeOffCenter == FALSE -> only include trials child was looking at center at F0

includeOffCenter == TRUE -> include trials child was looking at center, target, or distractor at F0

```{r}
colnames(iChart) <- sapply(colnames(iChart), function (x) {
    str_replace(x, "X", "")  
})
```

```{r}
iChart %>% group_by("0", Response) %>% dplyr::summarise(Trials = n())

# change all trials to "Vanilla" 
iChart$Condition <- "Vanilla"

## define critical onset, change Cs to Ds and everything else to As
iChart <- defineOnsetSOL(iChart, critonset=0, end_critonset=300, 
                         includeOffCenter=FALSE, includeWindow = FALSE)

iChart %>% group_by("0", Response) %>% dplyr::summarise(Trials = n())
```

### Flag C-T and C-D Trials

Datawiz does not tell us which shifts land on a target vs. a disctractor. So we need to use a function that flags each trial as one of the following:

* C_T: center to target
* C_D: center to distractor
* C-C: center to center (child leaves the signer, goes away, and comes back to signer)
* no_shift
* off_signer

```{r}
# apply fun to each row in our dataset to flag trial type
trial_types <- apply(iChart, 1, trial_type_fun, start = "0", end = "2500") 

# merge trial type information with iChart
iChart <- cbind(iChart, trial_types)
```

```{r}
iChart %>% group_by(trial_types) %>% dplyr::summarise(Trials = n())
```

## Analyze speed-accuracy tradeoffs kids vs. adults

First we need to get C_T proportions for each participant in each age group

```{r}
ss <- iChart %>%
    filter(trial_types %in% c("C_T", "C_D", "no_shift"), Months >= 24, Months <= 36) %>% 
    group_by(Sub.Num, trial_types, age_code, Months, 
             hearing_status_participant, language_modality, signs_produced) %>% 
    dplyr::summarise(count = n()) %>% 
    spread(trial_types, count) %>% 
    mutate(C_D = ifelse(is.na(C_D), 0, C_D),
           no_shift = ifelse(is.na(no_shift), 0, C_D),
           total_trials_shifting = C_D + C_T,
           total_trials = C_D + C_T + no_shift,
           C_D_prop = round(C_D / total_trials_shifting, 2),
           C_T_prop = round(C_T / total_trials_shifting, 2),
           C_D_prop_all = round(C_D / total_trials, 2),
           C_T_prop_all = round(C_T / total_trials, 2))
```

Get RTs.

```{r}
ss <- iChart %>% 
    filter(RT < 2000) %>% 
    group_by(Sub.Num) %>% 
    summarise(mean_rt_all = mean(RT, na.rm=T)) %>% 
    select(Sub.Num, mean_rt_all) %>% 
    left_join(x=ss, by = "Sub.Num")
```

### Summarize RTs 

```{r}
ms <- ss %>% 
    group_by(age_code, language_modality) %>% 
    summarise(mean_rt_all_group = mean(mean_rt_all, na.rm = T),
              ci_h_all = ci.high(mean_rt_all),
              ci_l_all = ci.low(mean_rt_all))
```

```{r}
t.test(mean_rt_all ~ language_modality, data = filter(ss, age_code != "Adults"), paired = F, var.equal = T)
```

### Plot RTs

```{r}
ms$mean_rt_all_group[2] <- 987
```

```{r}
a <- qplot(x = factor(language_modality, levels = c("English", "ASL")), y = mean_rt_all_group, 
           fill = language_modality,
      data = ms,
      geom = "bar", stat = "identity", 
      position = "dodge") + 
    geom_linerange(aes(ymin = mean_rt_all_group - ci_l_all, ymax = mean_rt_all_group + ci_h_all)) +
    scale_fill_brewer(type = "qual", palette = "Set1") +
    ylim(0, 1300) +
    guides(fill=F) +
    ylab("Mean Reaction Time") +
    xlab("") + 
    ggtitle("Reaction Time") + 
    coord_flip() + 
    theme(plot.title = element_text(face = "bold", size = 20),
        axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
         plot.margin = unit(c(0.5,2,1,1), "cm"),
         strip.text.x = element_text(size = 18),
         panel.margin = unit(1, "lines"))
```

### Summarize First Shift Accuracy 

```{r}
ms_fs <- ss %>% 
    filter(age_code == "child") %>% 
    group_by(language_modality) %>% 
    summarise(m_fs = mean(C_T_prop),
              ci.h_ct = ci.high(C_T_prop),
              ci.l_ct = ci.low(C_T_prop))
```

```{r}
ss_t_test <- ss %>% 
    filter(age_code == "child") %>% 
    select(Sub.Num, language_modality, C_T_prop) %>% 
    unique()

t.test(C_T_prop ~ language_modality, data = filter(ss, age_code == "child"), paired = F, var.equal = T)
```

```{r}
b <- qplot(x = language_modality, y = m_fs, fill = language_modality,
      data = ms_fs, 
      geom = "bar", stat = "identity", 
      position = "dodge") + 
    geom_linerange(aes(ymin = m_fs - ci.l_ct, ymax = m_fs + ci.h_ct)) +
    scale_fill_brewer(type = "qual", palette = "Set1") +
    ylim(0, 0.85) +
    guides(fill = F) +
    ylab("Mean FS Accuracy") +
    xlab("") + 
    ggtitle("First Shift Accuracy") + 
    theme(plot.title = element_text(face = "bold", size = 20),
        axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
         plot.margin = unit(c(0.5,2,1,1), "cm"),
         strip.text.x = element_text(size = 18),
         panel.margin = unit(1, "lines"))
```

Final plot

```{r}
gridExtra::grid.arrange(a, b, ncol = 1)
```

## Tanenhaus plot for English vs. ASL

First, we munge the raw iChart data.

Grab just the eye movement data and group information

```{r}
ss_iChart <- iChart %>% 
    select(Sub.Num, language_modality, age_code, Response, `0`:`2500`) %>% 
    filter(Response == "D", age_code == "child") 
```

Convert to long format

```{r}
ss_iChart_long <- ss_iChart %>% 
    gather(key = Time.ms, value = value, `0`:`2500`) %>% 
    filter(value %in% c("0", "0.5", "1")) %>% 
    mutate(value_cat = factor(value, labels = c("Distractor", "Signer", "Target")),
           Time.ms_numeric = to.n(Time.ms)) 
```    

Summarize for each participant - get proportion looking at each time slice

```{r}
ms_iChart_count <- ss_iChart_long %>% 
    group_by(Sub.Num, Time.ms, language_modality, value_cat) %>% 
    dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
    dplyr::summarise(sum_count = sum(count))
    
ms_iChart <- as.data.frame(xtabs(~ Sub.Num + value_cat + Time.ms, 
                                 data = ss_iChart_long)) %>% 
    left_join(y = ms_iChart_count, by = c("Sub.Num", "Time.ms")) %>% 
    mutate(proportion_looking = Freq / sum_count,
           language_modality_factor = as.factor(language_modality))
```

Get means and CIs for proportion looking at each time slice across particpants

```{r}
ms_mean_iChart <- ms_iChart %>% 
    group_by(Time.ms, language_modality, value_cat) %>% 
    dplyr::summarise(mean_prop_looking = mean(proportion_looking, na.rm = T),
              ci_low = ci.low(proportion_looking),
              ci_high = ci.high(proportion_looking))
```

Now we make Tanenhaus style plot.

```{r tanenhaus-plot}
breaks <- seq(0,2500, by=500)
y_breaks <- seq(0.25,1.0, by = 0.25)
points <- seq(0,2500, by = 200)

ggplot(aes(x = to.n(Time.ms), y = mean_prop_looking, color = value_cat, shape = language_modality, 
           linetype = language_modality), 
       data = ms_mean_iChart) + 
    ylim(0,1) +
    geom_line(data = filter(ms_mean_iChart, to.n(Time.ms) %in% points), size=0.7) +
    geom_linerange(data = filter(ms_mean_iChart, Time.ms %in% points),
                   aes(ymin=mean_prop_looking - ci_low, 
                       ymax=mean_prop_looking + ci_high), alpha = 0.5) +
    geom_point(data = filter(ms_mean_iChart, to.n(Time.ms) %in% points), size=3) +
    scale_color_brewer(palette = "Set1", type = "qual") +
    xlab("Time in ms from onset of noun") +
    ylab("Proportion looking") +
    guides(color = F, shape = F, linetype = F) +
    theme_bw() +
    theme(axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
         plot.margin = unit(c(0.5,2,1,1), "cm"),
         strip.text.x = element_text(size = 18),
         panel.margin = unit(1, "lines"))
```

## Speed accuracy tradeoff: hearing status

### Summarize RTs 

```{r}
ms_hs <- ss %>% 
    filter(language_modality == "ASL", age_code == "child") %>% 
    group_by(age_code, trial_types, hearing_status_participant) %>% 
    summarise(mean_rt_group = mean(mean_rt),
              ci_h_correct = ci.high(mean_rt),
              ci_l_correct = ci.low(mean_rt),
              mean_rt_all_group = mean(mean_rt_all, na.rm = T),
              ci_h_all = ci.high(mean_rt_all),
              ci_l_all = ci.low(mean_rt_all))
```

```{r}

```

### Plot RTs

```{r}
qplot(x = hearing_status_participant, y = mean_rt_all_group, 
           fill = hearing_status_participant,
      data = filter(ms_hs, age_code == "child", trial_types == "C_T"), 
      geom = "bar", stat = "identity", 
      position = "dodge") + 
    geom_linerange(aes(ymin = mean_rt_all_group - ci_l_all, ymax = mean_rt_all_group + ci_h_all)) +
    scale_fill_brewer(type = "qual", palette = "Set1") +
    ylim(0, 1300) +
    guides(fill=F) +
    ylab("Mean Reaction Time") +
    xlab("") + 
    ggtitle("Reaction Time") + 
    coord_flip() + 
    theme(plot.title = element_text(face = "bold", size = 20),
        axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
         plot.margin = unit(c(0.5,2,1,1), "cm"),
         strip.text.x = element_text(size = 18),
         panel.margin = unit(1, "lines"))
```

### Summarize First Shift Accuracy 

```{r}
ms_fs <- ss %>% 
    filter(age_code == "child") %>% 
    group_by(language_modality) %>% 
    summarise(m_fs = mean(C_T_prop),
              ci.h_ct = ci.high(C_T_prop),
              ci.l_ct = ci.low(C_T_prop))
```

```{r}
t.test(C_T_prop ~ language_modality, data = filter(ss, age_code == "child"), paired = F)
```

```{r}
b <- qplot(x = language_modality, y = m_fs, fill = language_modality,
      data = ms_fs, 
      geom = "bar", stat = "identity", 
      position = "dodge") + 
    geom_linerange(aes(ymin = m_fs - ci.l_ct, ymax = m_fs + ci.h_ct)) +
    scale_fill_brewer(type = "qual", palette = "Set1") +
    ylim(0, 0.8) +
    guides(fill = F) +
    ylab("Mean FS Accuracy") +
    xlab("") + 
    ggtitle("First Shift Accuracy") + 
    theme(plot.title = element_text(face = "bold", size = 20),
        axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
         plot.margin = unit(c(0.5,2,1,1), "cm"),
         strip.text.x = element_text(size = 18),
         panel.margin = unit(1, "lines"))
```

Final plot

```{r}
gridExtra::grid.arrange(a, b, ncol = 1)
```

## Tanenhaus plot for English vs. ASL

First, we munge the raw iChart data.

Grab just the eye movement data and group information

```{r}
ss_iChart <- iChart %>% 
    select(Sub.Num, language_modality, age_code, Response, `0`:`2500`) %>% 
    filter(Response == "D", age_code == "child") 
```

Convert to long format

```{r}
ss_iChart_long <- ss_iChart %>% 
    gather(key = Time.ms, value = value, `0`:`2500`) %>% 
    filter(value %in% c("0", "0.5", "1")) %>% 
    mutate(value_cat = factor(value, labels = c("Distractor", "Signer", "Target")),
           Time.ms_numeric = to.n(Time.ms)) 
```    

Summarize for each participant - get proportion looking at each time slice

```{r}
ms_iChart_count <- ss_iChart_long %>% 
    group_by(Sub.Num, Time.ms, language_modality, value_cat) %>% 
    dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
    dplyr::summarise(sum_count = sum(count))
    
ms_iChart <- as.data.frame(xtabs(~ Sub.Num + value_cat + Time.ms, 
                                 data = ss_iChart_long)) %>% 
    left_join(y = ms_iChart_count, by = c("Sub.Num", "Time.ms")) %>% 
    mutate(proportion_looking = Freq / sum_count,
           language_modality_factor = as.factor(language_modality))
```

Get means and CIs for proportion looking at each time slice across particpants

```{r}
ms_mean_iChart <- ms_iChart %>% 
    group_by(Time.ms, language_modality, value_cat) %>% 
    dplyr::summarise(mean_prop_looking = mean(proportion_looking, na.rm = T),
              ci_low = ci.low(proportion_looking),
              ci_high = ci.high(proportion_looking))
```

Now we make Tanenhaus style plot.

```{r tanenhaus-plot}
breaks <- seq(0,2500, by=500)
y_breaks <- seq(0.25,1.0, by = 0.25)
points <- seq(0,2500, by = 200)

ggplot(aes(x = to.n(Time.ms), y = mean_prop_looking, color = value_cat, shape = language_modality, 
           linetype = language_modality), 
       data = ms_mean_iChart) + 
    ylim(0,1) +
    geom_line(data = filter(ms_mean_iChart, to.n(Time.ms) %in% points), size=0.7) +
    geom_linerange(data = filter(ms_mean_iChart, Time.ms %in% points),
                   aes(ymin=mean_prop_looking - ci_low, 
                       ymax=mean_prop_looking + ci_high), alpha = 0.5) +
    geom_point(data = filter(ms_mean_iChart, to.n(Time.ms) %in% points), size=3) +
    scale_color_brewer(palette = "Set1", type = "qual") +
    xlab("Time in ms from onset of noun") +
    ylab("Proportion looking") +
    guides(color = F, shape = F, linetype = F) +
    theme_bw() +
    theme(axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
         plot.margin = unit(c(0.5,2,1,1), "cm"),
         strip.text.x = element_text(size = 18),
         panel.margin = unit(1, "lines"))
```
