---
title: "Speed-Accuracy Timecourse Plots"
author: "Kyle MacDonald"
date: "July, 12 2016"
output: html_document
---

```{r chunk_options, echo = F}
rm(list=ls()) # code to clear workspace

knitr::opts_chunk$set(warning=F, message=F, sanitize = T, 
                      fig.height=5, fig.width=8, echo=T, cache = T)


# devtools::install_github("langcog/langcog")
library(langcog)
library(magrittr)
library(RWiener)
library(stringr)
library(GGally)
library(kmr)
library(lme4)
library(lsr)
library(plyr)
library(gridExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
theme_set(theme_bw()) # set the ggplot theme that we think is pretty
```

## Load data

```{r load and clean up data}
d <- read.csv("../data/3_final_merged_data/speed-acc-cleaned-iChart.csv", 
              stringsAsFactors = F)

d %<>% mutate(stimuli = ifelse(stimuli == "V1" | stimuli == "V2", "ASL", 
                               ifelse(stimuli == "Trio", "Object", 
                                      ifelse(stimuli == "Bull", "Bullseye",
                                             stimuli))),
              stimuli = factor(stimuli, levels = c("ASL", "Face", "Object", "Bullseye")))

colnames(d) <- gsub(pattern = "X", replacement = "", x = colnames(d))
```

## Tanenhaus plot for English vs. ASL

First, we munge the raw iChart data.

Grab just the eye movement data and group information

```{r}
ss_iChart <- d %>% 
  select(Sub.Num, language_modality, trial_type, stimuli, age_code, Response, `0`:`3000`) %>% 
  filter(Response == "D", age_code == "child") 
```

Convert to long format

```{r}
ss_iChart_long <- ss_iChart %>% 
  gather(key = Time.ms, value = value, `0`:`3000`) %>% 
  filter(value %in% c("0", "0.5", "1")) %>% 
  mutate(value_cat = factor(value, labels = c("Distractor", "Signer", "Target")),
         Time.ms_numeric = as.numeric(Time.ms)) 
```    

Summarize for each participant - get proportion looking at each time slice

```{r}
ms_iChart_count <- ss_iChart_long %>% 
  group_by(Sub.Num, Time.ms, language_modality, value_cat) %>% 
  dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
  dplyr::summarise(sum_count = sum(count)) %>% 
  ungroup() %>% 
  mutate(Sub.Num = as.character(Sub.Num))

ms_iChart <- as.data.frame(xtabs(~ Sub.Num + value_cat + Time.ms, data = ss_iChart_long),
                           stringsAsFactors = F) %>% 
  left_join(y = ms_iChart_count, by = c("Sub.Num", "Time.ms")) %>% 
  mutate(proportion_looking = Freq / sum_count,
         language_modality_factor = as.factor(language_modality))
```

Get means and CIs for proportion looking at each time slice across particpants

```{r}
ms_mean_iChart <- ms_iChart %>% 
  group_by(Time.ms, language_modality, value_cat) %>% 
  multi_boot_standard(column = "proportion_looking", na.rm = T)
```

Now we make Tanenhaus style plot.

```{r tanenhaus-plot}
breaks <- seq(0,3000, by=500)
y_breaks <- seq(0.25,1.0, by = 0.25)
points <- seq(0,3000, by = 200)

ggplot(aes(x = as.numeric(Time.ms), y = mean, 
           color = value_cat, shape = language_modality, 
           linetype = language_modality), 
       data = ms_mean_iChart) + 
  ylim(0,1) +
  geom_line(data = filter(ms_mean_iChart, as.numeric(Time.ms) %in% points), size=0.7) +
  geom_linerange(data = filter(ms_mean_iChart, Time.ms %in% points),
                 aes(ymin=ci_lower, ymax=ci_upper), alpha = 0.5) +
  geom_point(data = filter(ms_mean_iChart, as.numeric(Time.ms) %in% points), size=3) +
  scale_color_brewer(palette = "Set1", type = "qual") +
  xlab("Time in ms from onset of noun") +
  ylab("Proportion looking") +
  guides(color = F, shape = F, linetype = F) +
  theme_bw() +
  theme(axis.title.x = element_text(colour="grey40",size=22,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="grey40",size=22,
                                    angle=90,hjust=0.5,vjust=0.5,face="plain"),
        axis.text.x = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        plot.margin = unit(c(0.5,2,1,1), "cm"),
        strip.text.x = element_text(size = 18),
        panel.margin = unit(1, "lines"))
```

## Same plot but separate by stimuli

```{r}
ms_iChart_count <- ss_iChart_long %>% 
  group_by(Sub.Num, Time.ms, stimuli, value_cat) %>% 
  dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
  dplyr::summarise(sum_count = sum(count)) %>% 
  ungroup() %>% 
  mutate(Sub.Num = as.character(Sub.Num))

ms_iChart <- as.data.frame(xtabs(~ Sub.Num + value_cat + Time.ms, data = ss_iChart_long),
                           stringsAsFactors = F) %>% 
  left_join(y = ms_iChart_count, by = c("Sub.Num", "Time.ms")) %>% 
  mutate(proportion_looking = Freq / sum_count,
         stimuli_factor = as.factor(stimuli))

ms_mean_iChart <- ms_iChart %>% 
  group_by(Time.ms, stimuli, value_cat) %>% 
  multi_boot_standard(column = "proportion_looking", na.rm = T) %>% 
  filter(is.na(stimuli) == F)
```

```{r tanenhaus-plot 2}
breaks <- seq(0,3000, by=500)
y_breaks <- seq(0.25,1.0, by = 0.25)
points <- seq(0,3000, by = 200)

# change factor levels for plot to help compare conditions of interest
ms_mean_iChart$stimuli <- factor(ms_mean_iChart$stimuli, 
                                 levels = c("ASL", "Object", "Face", "Bullseye"))

ggplot(aes(x = as.numeric(Time.ms), y = mean, 
           color = value_cat), 
       data = ms_mean_iChart) + 
  ylim(0,1) +
  geom_line(data = filter(ms_mean_iChart, as.numeric(Time.ms) %in% points), size=0.7) +
  geom_linerange(data = filter(ms_mean_iChart, Time.ms %in% points),
                 aes(ymin=ci_lower, ymax=ci_upper), alpha = 0.5) +
  geom_point(data = filter(ms_mean_iChart, as.numeric(Time.ms) %in% points), size=2) +
  scale_color_brewer(palette = "Set1", type = "qual") +
  xlab("Time in ms from onset of noun") +
  ylab("Proportion looking") +
  guides(color = F, shape = F, linetype = F) +
  theme_bw() +
  facet_wrap(~stimuli, ncol = 2) +
  theme(axis.title.x = element_text(colour="grey40",size=18,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="grey40",size=18,
                                    angle=90,hjust=0.5,vjust=0.5,face="plain"),
        axis.text.x = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        plot.margin = unit(c(0.5,2,1,1), "cm"),
        strip.text.x = element_text(size = 16),
        panel.margin = unit(1, "lines"))
```

## Timecourse plot split by trial type (C-T vs. C-D)

Goal: plot different curves for correct and incorrect shifting trials.