
### Plot RTs

```{r}
ms$mean_rt_all_group[2] <- 987
```

```{r}
a <- qplot(x = factor(language_modality, levels = c("English", "ASL")), y = mean_rt_all_group, 
           fill = language_modality,
           data = ms,
           geom = "bar", stat = "identity", 
           position = "dodge") + 
    geom_linerange(aes(ymin = mean_rt_all_group - ci_l_all, ymax = mean_rt_all_group + ci_h_all)) +
    scale_fill_brewer(type = "qual", palette = "Set1") +
    ylim(0, 1300) +
    guides(fill=F) +
    ylab("Mean Reaction Time") +
    xlab("") + 
    ggtitle("Reaction Time") + 
    coord_flip() + 
    theme(plot.title = element_text(face = "bold", size = 20),
          axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          plot.margin = unit(c(0.5,2,1,1), "cm"),
          strip.text.x = element_text(size = 18),
          panel.margin = unit(1, "lines"))
```

### Summarize First Shift Accuracy 

```{r}
ms_fs <- ss %>% 
    filter(age_code == "child") %>% 
    group_by(language_modality) %>% 
    summarise(m_fs = mean(C_T_prop),
              ci.h_ct = ci.high(C_T_prop),
              ci.l_ct = ci.low(C_T_prop))
```

```{r}
ss_t_test <- ss %>% 
    filter(age_code == "child") %>% 
    select(Sub.Num, language_modality, C_T_prop) %>% 
    unique()

t.test(C_T_prop ~ language_modality, data = filter(ss, age_code == "child"), paired = F, var.equal = T)
```

```{r}
b <- qplot(x = language_modality, y = m_fs, fill = language_modality,
           data = ms_fs, 
           geom = "bar", stat = "identity", 
           position = "dodge") + 
    geom_linerange(aes(ymin = m_fs - ci.l_ct, ymax = m_fs + ci.h_ct)) +
    scale_fill_brewer(type = "qual", palette = "Set1") +
    ylim(0, 0.85) +
    guides(fill = F) +
    ylab("Mean FS Accuracy") +
    xlab("") + 
    ggtitle("First Shift Accuracy") + 
    theme(plot.title = element_text(face = "bold", size = 20),
          axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          plot.margin = unit(c(0.5,2,1,1), "cm"),
          strip.text.x = element_text(size = 18),
          panel.margin = unit(1, "lines"))
```

Final plot

```{r}
gridExtra::grid.arrange(a, b, ncol = 1)
```

## Tanenhaus plot for English vs. ASL

First, we munge the raw iChart data.

Grab just the eye movement data and group information

```{r}
ss_iChart <- iChart %>% 
    select(Sub.Num, language_modality, age_code, Response, `0`:`2500`) %>% 
    filter(Response == "D", age_code == "child") 
```

Convert to long format

```{r}
ss_iChart_long <- ss_iChart %>% 
    gather(key = Time.ms, value = value, `0`:`2500`) %>% 
    filter(value %in% c("0", "0.5", "1")) %>% 
    mutate(value_cat = factor(value, labels = c("Distractor", "Signer", "Target")),
           Time.ms_numeric = to.n(Time.ms)) 
```    

Summarize for each participant - get proportion looking at each time slice

```{r}
ms_iChart_count <- ss_iChart_long %>% 
    group_by(Sub.Num, Time.ms, language_modality, value_cat) %>% 
    dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
    dplyr::summarise(sum_count = sum(count))

ms_iChart <- as.data.frame(xtabs(~ Sub.Num + value_cat + Time.ms, 
                                 data = ss_iChart_long)) %>% 
    left_join(y = ms_iChart_count, by = c("Sub.Num", "Time.ms")) %>% 
    mutate(proportion_looking = Freq / sum_count,
           language_modality_factor = as.factor(language_modality))
```

Get means and CIs for proportion looking at each time slice across particpants

```{r}
ms_mean_iChart <- ms_iChart %>% 
    group_by(Time.ms, language_modality, value_cat) %>% 
    dplyr::summarise(mean_prop_looking = mean(proportion_looking, na.rm = T),
                     ci_low = ci.low(proportion_looking),
                     ci_high = ci.high(proportion_looking))
```

Now we make Tanenhaus style plot.

```{r tanenhaus-plot}
breaks <- seq(0,2500, by=500)
y_breaks <- seq(0.25,1.0, by = 0.25)
points <- seq(0,2500, by = 200)

ggplot(aes(x = to.n(Time.ms), y = mean_prop_looking, color = value_cat, shape = language_modality, 
           linetype = language_modality), 
       data = ms_mean_iChart) + 
    ylim(0,1) +
    geom_line(data = filter(ms_mean_iChart, to.n(Time.ms) %in% points), size=0.7) +
    geom_linerange(data = filter(ms_mean_iChart, Time.ms %in% points),
                   aes(ymin=mean_prop_looking - ci_low, 
                       ymax=mean_prop_looking + ci_high), alpha = 0.5) +
    geom_point(data = filter(ms_mean_iChart, to.n(Time.ms) %in% points), size=3) +
    scale_color_brewer(palette = "Set1", type = "qual") +
    xlab("Time in ms from onset of noun") +
    ylab("Proportion looking") +
    guides(color = F, shape = F, linetype = F) +
    theme_bw() +
    theme(axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          plot.margin = unit(c(0.5,2,1,1), "cm"),
          strip.text.x = element_text(size = 18),
          panel.margin = unit(1, "lines"))
```

## Speed accuracy tradeoff: hearing status

### Summarize RTs 

```{r}
ms_hs <- ss %>% 
    filter(language_modality == "ASL", age_code == "child") %>% 
    group_by(age_code, trial_types, hearing_status_participant) %>% 
    summarise(mean_rt_group = mean(mean_rt),
              ci_h_correct = ci.high(mean_rt),
              ci_l_correct = ci.low(mean_rt),
              mean_rt_all_group = mean(mean_rt_all, na.rm = T),
              ci_h_all = ci.high(mean_rt_all),
              ci_l_all = ci.low(mean_rt_all))
```

### Plot RTs

```{r}
qplot(x = hearing_status_participant, y = mean_rt_all_group, 
      fill = hearing_status_participant,
      data = filter(ms_hs, age_code == "child", trial_types == "C_T"), 
      geom = "bar", stat = "identity", 
      position = "dodge") + 
    geom_linerange(aes(ymin = mean_rt_all_group - ci_l_all, ymax = mean_rt_all_group + ci_h_all)) +
    scale_fill_brewer(type = "qual", palette = "Set1") +
    ylim(0, 1300) +
    guides(fill=F) +
    ylab("Mean Reaction Time") +
    xlab("") + 
    ggtitle("Reaction Time") + 
    coord_flip() + 
    theme(plot.title = element_text(face = "bold", size = 20),
          axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          plot.margin = unit(c(0.5,2,1,1), "cm"),
          strip.text.x = element_text(size = 18),
          panel.margin = unit(1, "lines"))
```

### Summarize First Shift Accuracy 

```{r}
ms_fs <- ss %>% 
    filter(age_code == "child") %>% 
    group_by(language_modality) %>% 
    summarise(m_fs = mean(C_T_prop),
              ci.h_ct = ci.high(C_T_prop),
              ci.l_ct = ci.low(C_T_prop))
```

```{r}
t.test(C_T_prop ~ language_modality, data = filter(ss, age_code == "child"), paired = F)
```

```{r}
b <- qplot(x = language_modality, y = m_fs, fill = language_modality,
           data = ms_fs, 
           geom = "bar", stat = "identity", 
           position = "dodge") + 
    geom_linerange(aes(ymin = m_fs - ci.l_ct, ymax = m_fs + ci.h_ct)) +
    scale_fill_brewer(type = "qual", palette = "Set1") +
    ylim(0, 0.8) +
    guides(fill = F) +
    ylab("Mean FS Accuracy") +
    xlab("") + 
    ggtitle("First Shift Accuracy") + 
    theme(plot.title = element_text(face = "bold", size = 20),
          axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          plot.margin = unit(c(0.5,2,1,1), "cm"),
          strip.text.x = element_text(size = 18),
          panel.margin = unit(1, "lines"))
```

Final plot

```{r}
gridExtra::grid.arrange(a, b, ncol = 1)
```

## Tanenhaus plot for English vs. ASL

First, we munge the raw iChart data.

Grab just the eye movement data and group information

```{r}
ss_iChart <- iChart %>% 
    select(Sub.Num, language_modality, age_code, Response, `0`:`2500`) %>% 
    filter(Response == "D", age_code == "child") 
```

Convert to long format

```{r}
ss_iChart_long <- ss_iChart %>% 
    gather(key = Time.ms, value = value, `0`:`2500`) %>% 
    filter(value %in% c("0", "0.5", "1")) %>% 
    mutate(value_cat = factor(value, labels = c("Distractor", "Signer", "Target")),
           Time.ms_numeric = to.n(Time.ms)) 
```    

Summarize for each participant - get proportion looking at each time slice

```{r}
ms_iChart_count <- ss_iChart_long %>% 
    group_by(Sub.Num, Time.ms, language_modality, value_cat) %>% 
    dplyr::summarise(count = ifelse(n() == 0, 0, n())) %>% 
    dplyr::summarise(sum_count = sum(count))

ms_iChart <- as.data.frame(xtabs(~ Sub.Num + value_cat + Time.ms, 
                                 data = ss_iChart_long)) %>% 
    left_join(y = ms_iChart_count, by = c("Sub.Num", "Time.ms")) %>% 
    mutate(proportion_looking = Freq / sum_count,
           language_modality_factor = as.factor(language_modality))
```

Get means and CIs for proportion looking at each time slice across particpants

```{r}
ms_mean_iChart <- ms_iChart %>% 
    group_by(Time.ms, language_modality, value_cat) %>% 
    dplyr::summarise(mean_prop_looking = mean(proportion_looking, na.rm = T),
                     ci_low = ci.low(proportion_looking),
                     ci_high = ci.high(proportion_looking))
```

Now we make Tanenhaus style plot.

```{r tanenhaus-plot}
breaks <- seq(0,2500, by=500)
y_breaks <- seq(0.25,1.0, by = 0.25)
points <- seq(0,2500, by = 200)

ggplot(aes(x = to.n(Time.ms), y = mean_prop_looking, color = value_cat, shape = language_modality, 
           linetype = language_modality), 
       data = ms_mean_iChart) + 
    ylim(0,1) +
    geom_line(data = filter(ms_mean_iChart, to.n(Time.ms) %in% points), size=0.7) +
    geom_linerange(data = filter(ms_mean_iChart, Time.ms %in% points),
                   aes(ymin=mean_prop_looking - ci_low, 
                       ymax=mean_prop_looking + ci_high), alpha = 0.5) +
    geom_point(data = filter(ms_mean_iChart, to.n(Time.ms) %in% points), size=3) +
    scale_color_brewer(palette = "Set1", type = "qual") +
    xlab("Time in ms from onset of noun") +
    ylab("Proportion looking") +
    guides(color = F, shape = F, linetype = F) +
    theme_bw() +
    theme(axis.title.x = element_text(colour="grey40",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="grey40",size=22,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          plot.margin = unit(c(0.5,2,1,1), "cm"),
          strip.text.x = element_text(size = 18),
          panel.margin = unit(1, "lines"))
```
